### 2020-07-21 tex/results.tex
add some context and cube figure

%!TEX root = ClementiBarba2020.tex

These first set of results correspond to the replication study of some results 
of Rockstuhl et al, 2005 \cite{rockstuhl2005}. Rockstuhl and coworkers did a two dimension 
study of the phonon-polariton response of different nanoparticles of silicon carbide (SiC)
using a 2D boundary element method. Their limit their study to 2D shapes and assumed an infinite
third dimension. (They solved full maxwell in 2D)

We count with a 3D surface boundary element method solver, that uses the electrostatic approximation
($\lambda > d$ where $d$ is the characteristic length of the geometry).

Initially we attempted to perform a convergence study on the result of Figure 18a
of Rockstuhl and coworkers. This simulation consists on a "quadratic cylinder" (square)
of size $L=535$. We tried to perform convergence on a cube of the same size L, but
due to the due to the sharp edges of the geometry we were not able to see proper convergence. 
However, we did a grid independence study. We were able to show that going from a mesh of 15552 
triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
triangles the simulations did not change at all (see Figure ).

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Extinction cross section divided by $L^2$ as a function fo wavelength divided by $L$ of
    a cube of size L=535 nm}
    \label{fig:cube535}
 \end{figure}

### 2020-07-21 tex/results.tex
add results on rockstuhl

@@
 
+{\color{red}We initially produced the meshes with trimesh (not sure how to cite), later we stick to 
+our own script}
+
 Initially we attempted to perform a convergence study on the result of Figure 18a
@@
 triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
-triangles the simulations did not change at all (see Figure ).
+triangles the simulations did not change at all (see Figure \ref{fig:cube535}).
 
@@
  \end{figure}
+
+In this results we see extra peaks that we believe is due to the nature of our 3D model, in this case 
+we have not extended the third dimension to approximate "infinity", but we suspect the extra peaks are 
+due to sharpness of the edges (they mention this on their paper too) as well as the 3D nature of our solver.
+
+These figure doesn't have the results digitized from the paper, but if needed we can add them.
+
+Based on these results we used the density of the cube as a reference to produce the meshes for the replication 
+of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). This simulation is a "rectangular cylinder" of 
+dimensions (we chose a case that will go well with our quasistatic model) are $a=672$ nm and $b=328$ nm.
+
+Effect of extended third dimension (in our case this is the y axis) are in Figures \ref{fig:ext_y_14a} and
+\ref{fig:ext_y_14b}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{ext_y_14a.pdf} 
+    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
+    short edge configuration (electric field parallel to the shorter dimension)}
+    \label{fig:ext_y_14a}
+ \end{figure}
+
+ \begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{ext_y_14b.pdf} 
+    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
+    long edge configuration (electric field parallel to the longer dimension)}
+    \label{fig:ext_y_14b}
+ \end{figure}
+
+We see that as we elongate the third dimension the extra peaks start fading.
+
+At this point we noticed that the mesher (trimesh) was not generating a uniform mesh. We created our 
+own mesher, and tested the difference. Moreover, the paper mentioned that they rounded the corners of their
+"rectangular cylinder". We were able to give our mesh as input to trimesh and round the edges but we were not able 
+to know how the roundness was related to the arc of the curvature. This were parameters with no physical meaning, 
+therefore we decided to go with the default setting.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{tri_reg_round_14a.pdf} 
+    \caption{Normalized (by max) Extinction cross section of a rectangle. Original trimesh, regular, and regular with 
+    roundness. Short edge configuration (electric field parallel to the shorter dimension)}
+    \label{fig:tri_reg_round_14a}
+ \end{figure}
+
+ \begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{tri_reg_round_14b.pdf} 
+    \caption{Normalized (by max) Extinction cross section of a rectangle.  Original trimesh, regular, and regular with 
+    roundness. Long edge configuration (electric field parallel to the longer dimension)}
+    \label{fig:tri_reg_round_14b}
+ \end{figure}
+
+ Finally with all this info, here is the replication of Figures 14a and 14b.
+
+ \begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{replication_14a.pdf} 
+    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of 
+    the short edge configuration (electric field parallel to the shorter dimension)}
+    \label{fig:rep_14a}
+ \end{figure}
+
+ \begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{replication_14b.pdf} 
+    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of the 
+    long edge configuration (electric field parallel to the longer dimension)}
+    \label{fig:rep_14b}
+ \end{figure}

### 2020-07-22 tex/results.tex
add results for nature case

@@
 %!TEX root = ClementiBarba2020.tex
+
+\section{Rockstuhl replication}
 
@@
  \end{figure}
+
+ \section{Ellis replication and validation}
+
+There are two results from this paper that we aim to replicate, and one of them is a comparison
+against experimental results which will lead to a validation.
+
+The first result we show is a replication of a result presented in their supplementary 
+material FigureS4 {\color{red}(note sure how to cite this, maybe a link)}. We aimed to replicate the 
+black curve since the simulation setup is possible to replicate using PyGBe. For each aspect ratio (AR) 
+value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
+800-1000 $cm^{-1}$, we identify the the lower frequency mode ($E_{100}$ in Ellis paper)  that is not a 
+longitudinal mode. We identify the Longitudinal modes by comparing normal vs 22 deg incidence runs. These
+modes due to its nature do not show up in the normal incidence runs. Then, on the 22 deg incidence 
+computations we choose the lower wave number mode that it's not a longitudinal mode. The simulations were 
+performed for the Long Edge orientation, meaning that the electric field is polarized along the long edge 
+of the pillar that is not the height.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{AR_22_vs_norm.pdf} 
+    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
+             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
+            Normalized by maximum extinction cross section as a function of wave number,
+            for a pillar orientation such that the electric field is parallel polarized 
+            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
+            We present the results for normal incidence and 22 degrees incidence, 
+            for different aspect ratios (AR)
+            }
+    \label{fig:AR_22_vs_norm}
+ \end{figure}
+
+THIS ARE THE PEAKS OF FIGURE \ref{fig:AR_22_vs_norm} need to find a better way of 
+present these numbers.
+
+AR 1 peaks at frequency\\
+normal: [ {\color{green}917.73} 934.092 949.604 957.325]\\
+22 deg: [ {\color{red}883.926} {\color{green}917.73} 935.052 949.604 957.325]\\
+
+AR 2 peaks at frequency\\
+normal: [ {\color{green}903.233} 926.395 944.762 958.242]\\
+22 deg: [ {\color{red}896.517} {\color{green}903.233} 926.395 944.762 958.242]\\
+
+AR 3 peaks at frequency\\
+normal: [ {\color{green}888.793} 922.552 931.223 948.613 958.242]\\
+22 deg: [ {\color{green}888.793} 899.418 922.552 931.223 958.242]\\
+
+AR 4 peaks at frequency\\
+normal: [ {\color{green}876.186} 929.32 946.639 958.242]\\
+22 deg: [ {\color{green}876.186} 901.281 921.618 929.32 945.745 958.242]\\
+
+AR 5 peaks at frequency\\
+normal: [ {\color{green}865.576} 926.395 945.745 958.242]\\
+22 deg: [ {\color{green}865.576} 901.281 921.618 958.242]\\
+
+AR 6 peaks at frequency\\
+normal: [ {\color{green}856.904} 914.793 923.489 929.32 946.639 958.242]\\
+22 deg: [ {\color{green}856.904} 901.281 920.6 958.242]\\
+
+AR 7 peaks at frequency
+normal: [ {\color{green}850.134} 910.963 921.618 928.372 946.639 958.242]
+22 deg: [ {\color{green}850.134} 901.281 910.963 920.6 958.242]
+
+In other words, we choose the lower mode (lower wavenumber) from the normal 
+incidence cases.
+
+Our simulations differ on the method and we do not have a substrate included. The black curve on 
+Ellis et al \cite{ellis2016} represents the resonance positions for the $E_{100}$ mode for the different 
+aspect ratios when the pillar are separated by a 5000 nm gap. The simulations performed with \pygbe 
+consist of one isolated pillar.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
+    \caption{Replication of figure S4 of supplementary material of Ellis 2016}
+    \label{fig:rep_FS4_ellis}
+ \end{figure}
+
+ If we calculate de relative percentage error for each of these points we get:
+
+ \begin{table}
+    \centering
+    \caption{\label{table:err_AR} Percentage error for different aspect ratios.} 
+    \begin{tabular}{c c}
+    \hline%\toprule
+    ARR & \% error \\
+    \hline%\midrule
+     $1$ & $0.95$ \\
+     $2$ & $0.67$ \\
+     $3$ & $0.35$ \\
+     $4$ & $0.16$ \\
+     $5$ & $0.72$ \\
+     $6$ & $1.20$ \\
+     $7$ & $1.59$ \\
+    \hline%\bottomrule
+    \end{tabular}
+\end{table}
+
+\pygbe AR=4 attempt of validation Figure 2a (see Figure \ref{fig:pygbe_vs_exp_2a})
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
+    \caption{\pygbe vs experiments, figure 2a of Ellis 2016. Ellis et al 
+    has near field interaction in its experiments. Ellis data was digitized
+    with web digitizer.}
+    \label{fig:pygbe_vs_exp_2a}
+ \end{figure}
+
+First order approximation to achieve validation. In our code we do not have near 
+field interaction. From Figure S4 in supplementary material of Ellis et al. We know that 
+for the first mode ($E_{100}$) the difference between interaction and no interaction is 
+12.17 $cm^{-1}$ (obtained from digitized data). If we use this as a first order approximation,
+we can subtract that value from our curve, and the results are in Figure \ref{fig:val_2a}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{validation_FOA_fig2a_Ellis.pdf} 
+    \caption{Validation against experiments in figure 2a of Ellis 2016, using first order approximation}
+    \label{fig:val_2a}
+ \end{figure}
+
+If we use the same approximation and compare the results with Ellis simulations on
+Figure 2 of their paper (green curve) we get (see Figure \ref{fig:rep_2a})
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{replication_FOA_fig2a_Ellis.pdf} 
+    \caption{Replication of simulations in figure 2a of Ellis 2016, using first
+     order approximation}
+    \label{fig:rep_2a}
+ \end{figure}

### 2020-07-22 tex/results.tex
fix fig size
better caption for grid independence

@@
     \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
-    \caption{Extinction cross section divided by $L^2$ as a function fo wavelength divided by $L$ of
-    a cube of size L=535 nm}
+    \caption{Grid independence study for a SiC cube of side L=535 nm, in air under a constant 
+    electric field in the z-direction. Extinction cross section divided by $L^2$ as a function of wavelength divided 
+    by $L$ of a cube of size L=535 nm}
     \label{fig:cube535}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
+    \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
     \caption{Replication of figure S4 of supplementary material of Ellis 2016}

### 2020-07-22 tex/results.tex
Better captions for figure

@@
     \includegraphics[width=0.85\textwidth]{ext_y_14a.pdf} 
-    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
+    \caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
+            Attempt of replication of Figure 14 a on Rockstuhl paper (case a1). In this case we have the constant 
+            electric field parallel to the short dimension (b), and the geometry is in air. 
+            Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
             short edge configuration (electric field parallel to the shorter dimension)}
@@
     \includegraphics[width=0.85\textwidth]{ext_y_14b.pdf} 
-    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
+    \caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
+    Attempt of replication of Figure 14b on Rockstuhl paper (case a1). In this case we have the constant 
+    electric field parallel to the long dimension (a), and the geometry is in air.
+        Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
     long edge configuration (electric field parallel to the longer dimension)}

### 2020-07-23 tex/results.tex
join figures that goe in pairs

--- 2020-07-22 tex/results.tex
@@
 
-Effect of extended third dimension (in our case this is the y axis) are in Figures \ref{fig:ext_y_14a} and
-\ref{fig:ext_y_14b}
+Effect of extended third dimension (in our case this is the y axis) are in Figures \ref{fig:ext_y_14} and
 
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{ext_y_14a.pdf} 
-    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
-    short edge configuration (electric field parallel to the shorter dimension)}
-    \label{fig:ext_y_14a}
+    \includegraphics[width=0.45\textwidth]{rockstuhl_rectangles.pdf} 
+    \caption{Rockstuhl runs configurations}
+    \label{fig:rectangle_sketch}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{ext_y_14b.pdf} 
-    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
-    long edge configuration (electric field parallel to the longer dimension)}
-    \label{fig:ext_y_14b}
+    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14a.pdf}}
+    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14b.pdf}} 
+    %\caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
+    %        Attempt of replication of Figure 14 a on Rockstuhl paper (case a1). In this case we have the constant 
+    %        electric field parallel to the short dimension (b), and the geometry is in air. 
+    %        Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
+    %        short edge configuration (electric field parallel to the shorter dimension)}
+    %\label{fig:ext_y_14a}
+    %\label{fig:ext_y_14b}
+    \caption{THIS IS A BIG CAPTION}
+    \label{fig:ext_y_14}   
  \end{figure}
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{tri_reg_round_14a.pdf} 
+    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14a.pdf}}
+    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14b.pdf}}
     \caption{Normalized (by max) Extinction cross section of a rectangle. Original trimesh, regular, and regular with 
-    roundness. Short edge configuration (electric field parallel to the shorter dimension)}
-    \label{fig:tri_reg_round_14a}
- \end{figure}
-
- \begin{figure}
-    \centering
-    \includegraphics[width=0.85\textwidth]{tri_reg_round_14b.pdf} 
-    \caption{Normalized (by max) Extinction cross section of a rectangle.  Original trimesh, regular, and regular with 
-    roundness. Long edge configuration (electric field parallel to the longer dimension)}
-    \label{fig:tri_reg_round_14b}
+    roundness. Short edge configuration (electric field parallel to the shorter (left) dimension)}
+    \label{fig:tri_reg_round_14}
  \end{figure}
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{replication_14a.pdf} 
+    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14a.pdf}}
+    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14b.pdf}}
+
     \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of 
-    the short edge configuration (electric field parallel to the shorter dimension)}
-    \label{fig:rep_14a}
- \end{figure}
-
- \begin{figure}
-    \centering
-    \includegraphics[width=0.85\textwidth]{replication_14b.pdf} 
-    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of the 
-    long edge configuration (electric field parallel to the longer dimension)}
-    \label{fig:rep_14b}
+    the short (long) edge configuration (electric field parallel to the shorter (longer) dimension)}
+    \label{fig:rep_14}
  \end{figure}
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{AR_22_vs_norm.pdf} 
+    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
     \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 

### 2020-07-23 tex/results.tex
Finally got the table to work

@@
 
-THIS ARE THE PEAKS OF FIGURE \ref{fig:AR_22_vs_norm} need to find a better way of 
-present these numbers.
+\begin{table}
+    \begin{center}
+      \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
+      field is parallel to the length (L) of the pillar. We have normal incidence and 22 degrees.}
+      \label{tab:table1}
+      \begin{tabular}{c c c c c c c c}
+        \textbf{AR} \\
+        \hline
+        \multirow{2}{*}{1} & $\perp$ & \textbf{917.73} & 934.092 & 949.604 & 957.325 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+        & 22$^{\circ}$ & 883.926 & \textbf{917.73} & 935.052 & 949.604 & 957.325 \\ % <-- Content of first column omitted.
+        \hline
+        \multirow{2}{*}{2} & $\perp$ & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+        & 22$^{\circ}$ & 896.517 & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Content of first column omitted.
+        \hline
+        \multirow{2}{*}{3} & $\perp$ & \textbf{888.793} & 922.552 & 931.223 & 948.613 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+        & 22$^{\circ}$ & \textbf{888.793} & 899.418 & 922.552 & 931.223 & 958.242 \\ % <-- Content of first column omitted.
+        \hline
+        \multirow{2}{*}{4} & $\perp$ & \textbf{876.186} & 929.32 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+        & 22$^{\circ}$ & \textbf{876.186} & 901.281 & 921.618 & 929.32 & 945.745 & 958.242 \\ % <-- Content of first column omitted.
+        \hline
+        \multirow{2}{*}{5} & $\perp$ & \textbf{865.576} & 926.395 & 945.745 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+        & 22$^{\circ}$ & \textbf{865.576} & 901.281 & 921.618 & 958.242 \\ % <-- Content of first column omitted.
+        \hline
+        \multirow{2}{*}{6} & $\perp$ &  \textbf{856.904} & 914.793 & 923.489 & 929.32 & 946.639 & 958.242\\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+        & 22$^{\circ}$ & \textbf{856.904} & 901.281 & 920.6 & 958.242\\ % <-- Content of first column omitted.
+        \hline
+        \multirow{2}{*}{7} & $\perp$ &  \textbf{850.134} & 910.963 & 921.618 & 928.372 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+        & 22$^{\circ}$ & \textbf{850.134} & 901.281 & 910.963 & 920.6 & 958.242\\ % <-- Content of first column omitted.
+        \hline
 
-AR 1 peaks at frequency\\
-normal: [ {\color{green}917.73} 934.092 949.604 957.325]\\
-22 deg: [ {\color{red}883.926} {\color{green}917.73} 935.052 949.604 957.325]\\
-
-AR 2 peaks at frequency\\
-normal: [ {\color{green}903.233} 926.395 944.762 958.242]\\
-22 deg: [ {\color{red}896.517} {\color{green}903.233} 926.395 944.762 958.242]\\
-
-AR 3 peaks at frequency\\
-normal: [ {\color{green}888.793} 922.552 931.223 948.613 958.242]\\
-22 deg: [ {\color{green}888.793} 899.418 922.552 931.223 958.242]\\
-
-AR 4 peaks at frequency\\
-normal: [ {\color{green}876.186} 929.32 946.639 958.242]\\
-22 deg: [ {\color{green}876.186} 901.281 921.618 929.32 945.745 958.242]\\
-
-AR 5 peaks at frequency\\
-normal: [ {\color{green}865.576} 926.395 945.745 958.242]\\
-22 deg: [ {\color{green}865.576} 901.281 921.618 958.242]\\
-
-AR 6 peaks at frequency\\
-normal: [ {\color{green}856.904} 914.793 923.489 929.32 946.639 958.242]\\
-22 deg: [ {\color{green}856.904} 901.281 920.6 958.242]\\
-
-AR 7 peaks at frequency
-normal: [ {\color{green}850.134} 910.963 921.618 928.372 946.639 958.242]
-22 deg: [ {\color{green}850.134} 901.281 910.963 920.6 958.242]
+      \end{tabular}
+    \end{center}
+  \end{table}
 

### 2020-07-23 tex/background.tex
add background.tex

%!TEX root = ClementiBarba2020.tex

\subsection{Verification, validation, reproducibility and replication}

\subsection{Description of the PyGBe software}

\subsection{Physics context for this work}

### 2020-07-23 tex/results.tex
rework sections
add context for rockstuhl work

@@
 
-\section{Rockstuhl replication}
+\subsection{Replication of results from Rockstuhl, et al., 2005}
+
+%%% Rockstuhl work summary%%%%
+The work of Rockstuhl et al. study the phonon-polariton response of silicon carbide (SiC)
+nanoparticles using the boundary element method. They analyze different "cylindrical particles"
+made of 6H-SiC as a function of geometrical cross section. These "cylinders" have an infinite
+extension in the third dimension, and they solve these geometries numerically with a 2D 
+boundary element method from their previous work \cite{rockstuhl2003}. 
+%%% Rockstuhl work summary%%%%
+
+We decided to replicate one of the results that they present on Fig.14 of their paper, which 
+presents the scattering cross section of a SiC rectangular cylinder for three different object 
+sizes. To complain with our quasistatic approach we chose the particular case where a=672 nm and 
+b=328 nm.
+
+\textbf{difference between methods, mesh and dielectric data}
+
+\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem, 
+while we solve a 3D model. In our case the geometry has a finite third dimension. To cope with this
+we will extend the third direction considerably, and study this effect.
+
+\textit{mesh}: Their work does not provide any details regarding the discretization of their geometries or 
+parameters involved in the simulations. We performed a grid independence study to make sure that we are
+solving properly the physics and minimizing errors due to discretization.
+
+\textit{dielectric data}: The use 6H-SiC as material, and they obtained their data from a a source that we
+were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
+via private communications.
 
@@
 
- \section{Ellis replication and validation}
+ \subsection{Replication of results from Ellis et al., 2016, and validation}
 

### 2020-07-23 tex/results.tex
Add more writing on grid independance study

@@
 %%% Rockstuhl work summary%%%%
-The work of Rockstuhl et al. study the phonon-polariton response of silicon carbide (SiC)
+The work of Rockstuhl et al.\cite{rockstuhl2005} study the phonon-polariton response of silicon carbide (SiC)
 nanoparticles using the boundary element method. They analyze different "cylindrical particles"
@@
 presents the scattering cross section of a SiC rectangular cylinder for three different object 
-sizes. To complain with our quasistatic approach we chose the particular case where a=672 nm and 
-b=328 nm.
+sizes. To complain with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
+case where a=672 nm and b=328 nm.
 
-\textbf{difference between methods, mesh and dielectric data}
+\textbf{Difference between methods, mesh and dielectric data}
 
@@
 we will extend the third direction considerably, and study this effect.
+We compute extinction cross section (scattering plus absorption) while Rockstuhl work present only scattering. 
+But since in both scattering and absorption the resonance occur at the same wavelengths, the results are 
+comparable.
 
@@
 
-These first set of results correspond to the replication study of some results 
-of Rockstuhl et al, 2005 \cite{rockstuhl2005}. Rockstuhl and coworkers did a two dimension 
-study of the phonon-polariton response of different nanoparticles of silicon carbide (SiC)
-using a 2D boundary element method. Their limit their study to 2D shapes and assumed an infinite
-third dimension. (They solved full maxwell in 2D)
+\subsubsection{Grid independance study}
 
-We count with a 3D surface boundary element method solver, that uses the electrostatic approximation
-($\lambda > d$ where $d$ is the characteristic length of the geometry).
-
-{\color{red}We initially produced the meshes with trimesh (not sure how to cite), later we stick to 
-our own script}
-
-Initially we attempted to perform a convergence study on the result of Figure 18a
-of Rockstuhl and coworkers. This simulation consists on a "quadratic cylinder" (square)
-of size $L=535$. We tried to perform convergence on a cube of the same size L, but
-due to the due to the sharp edges of the geometry we were not able to see proper convergence. 
-However, we did a grid independence study. We were able to show that going from a mesh of 15552 
+We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
+constant electric field aligned with the z-axis.
+(similar to quadratic cylinder on Fig 18 of Rockstuhl et.al). 
+Due to the nature of the geometry, and its sharp edges it was challenging to see proper convergence. However,
+for this type of physics, convergence has been studied in our previous work \cite{ClementiCooperBarba2019}. 
+In the Figure \ref{fig:cube535} we show a grid independence study, where we go from a mesh of 15552 
 triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
-triangles the simulations did not change at all (see Figure \ref{fig:cube535}).
+triangles and the computed results do not change.
 
@@
     \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
-    \caption{Grid independence study for a SiC cube of side L=535 nm, in air under a constant 
-    electric field in the z-direction. Extinction cross section divided by $L^2$ as a function of wavelength divided 
-    by $L$ of a cube of size L=535 nm}
+    \caption{Grid independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
+    electric field in the z-direction. The curves represent the extinction cross section divided by $L^2$ 
+    as a function of wavelength divided by $L$}
     \label{fig:cube535}
@@
 
-In this results we see extra peaks that we believe is due to the nature of our 3D model, in this case 
-we have not extended the third dimension to approximate "infinity", but we suspect the extra peaks are 
-due to sharpness of the edges (they mention this on their paper too) as well as the 3D nature of our solver.
+It is worth noting that the extinction cross section curve in Figure \ref{fig:cube535} has extra peaks, 
+compared to the results of Figure 18 on Rockstuhl, this is due to the 3D nature of our case and the sharp 
+edges. This will be approach in the following results where we attempt a replication of one of teh results 
+of Figure 14 of Rockstuhl work.
 
-These figure doesn't have the results digitized from the paper, but if needed we can add them.
+\subsubsection{Replication of Figure 14 (case a1) of Rockstuhl 2005}
 
-Based on these results we used the density of the cube as a reference to produce the meshes for the replication 
+Based on the reuslts of the grid independence stud we decided to we used the density of the cube as a reference to produce the meshes for the replication 
 of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). This simulation is a "rectangular cylinder" of 

### 2020-07-23 tex/results.tex
add more context and explanations on rockstuhl

@@
 presents the scattering cross section of a SiC rectangular cylinder for three different object 
-sizes. To complain with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
+sizes. To comply with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
 case where a=672 nm and b=328 nm.
@@
 
-Based on the reuslts of the grid independence stud we decided to we used the density of the cube as a reference to produce the meshes for the replication 
-of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). This simulation is a "rectangular cylinder" of 
-dimensions (we chose a case that will go well with our quasistatic model) are $a=672$ nm and $b=328$ nm.
+We chose to replicate the result of Rocksuthl et al. presented in Figure 14. In particular the case where $a=672$ nm 
+and $b=328$ nmn, since these dimension comply with the requirements of the quasistatic approximation.
+They present the normalized scattering cross section of a SiC rectangular cylinder, and they perform simulation 
+for two different setups. In Rockstuhl Figure 14 (left) they have the wave vector (illumination) along the long 
+side of the geometry, which means that the electric field is parallel to the short side of the rectangle. Following, 
+a similar analysis Rockstuhl Figure 14 (right) they have the wave vector (illumination) along the short
+side of the geometry, which means that the electric field is parallel to the long side of the rectangle. These orientations,
+correspond to the images (A) and (B) in the sketch presented in Figure \ref{fig:rectangle_sketch}.
 
-Effect of extended third dimension (in our case this is the y axis) are in Figures \ref{fig:ext_y_14} and
+Based on the results of the grid independence stud we decided to we used the density of the cube as a reference to 
+produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
+dimension we needed to chose a value that represents "infinity". To achieve this, we perform a study on the effects of 
+elongate the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different values of the 
+third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). 
+We see that as we extend the third dimension the intensity of some peaks decreases, this is because some
+of the peaks are related to the third dimension. Therefore, from now on we use $y=y=2688$ nm. It is worth 
+noting that we could have increased this value more, however, the simulations will become computational
+more expensive and we will still have the effects of having a 3D model.
 
@@
     \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14b.pdf}} 
-    %\caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
-    %        Attempt of replication of Figure 14 a on Rockstuhl paper (case a1). In this case we have the constant 
-    %        electric field parallel to the short dimension (b), and the geometry is in air. 
-    %        Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
-    %        short edge configuration (electric field parallel to the shorter dimension)}
-    %\label{fig:ext_y_14a}
-    %\label{fig:ext_y_14b}
-    \caption{THIS IS A BIG CAPTION}
+    \caption{Effect of the elongation of the third direction ($y$) on the 
+        extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm 
+        and $b=328$ nm, submerged in air and under a constant electric field 
+        parallel to the z-axis. The left plot corresponds to a configuration such that the electric 
+        field is parallel to $b$ (configuration (A) on Figure \ref{fig:rectangle_sketch}), while the 
+        right plot corresponds to a configuration such that the electric field is 
+        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}}
     \label{fig:ext_y_14}   
@@
 
-We see that as we elongate the third dimension the extra peaks start fading.
-
-At this point we noticed that the mesher (trimesh) was not generating a uniform mesh. We created our 
-own mesher, and tested the difference. Moreover, the paper mentioned that they rounded the corners of their
-"rectangular cylinder". We were able to give our mesh as input to trimesh and round the edges but we were not able 
-to know how the roundness was related to the arc of the curvature. This were parameters with no physical meaning, 
-therefore we decided to go with the default setting.
+To generate the meshes for these simulations, we used the open source software Trimesh 
+(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
+uniform mesh and that it was not possible to produce regular triangles with the functions 
+available. To overcome this, we created our own mesh using python scripts, and therefore 
+obtain uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
+on rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
+as a factor that will introduce extra peaks on the response. We were not able to control the 
+roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
+decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
+results on the effect of uniformity and roundness. You can see that the second peak is not
+present in the green curve, which can be attributed to the effect of the roundness. This is 
+consistent with the results on Rockstuhl's work.
 
@@
     \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14b.pdf}}
-    \caption{Normalized (by max) Extinction cross section of a rectangle. Original trimesh, regular, and regular with 
-    roundness. Short edge configuration (electric field parallel to the shorter (left) dimension)}
+    \caption{ Effect of uniformity and roundness on the mesh on the 
+    extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm, 
+    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
+    parallel to the z-axis}
     \label{fig:tri_reg_round_14}
@@
 
- Finally with all this info, here is the replication of Figures 14a and 14b.
+Once we have found the "best" possible geometry approximation, we show how our results 
+(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
+with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
+the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
+presented in Figure \ref{fig:rep_14}. We can say that the main peaks presented in Rockstuhl et al. are 
+successfully replicated. While we still have the presence of a third peak in our results, we believe 
+this is a consequence of the 3D nature of our geometry.
 
@@
     \subfloat{\includegraphics[width=0.45\textwidth]{replication_14b.pdf}} 
-
-    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of 
-    the short (long) edge configuration (electric field parallel to the shorter (longer) dimension)}
+    \caption{Replication of Figure 14 from Rockstuhl 2005. Extinction cross section of a
+    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
+    in air and under a constant electric field parallel to the z-axis.}
     \label{fig:rep_14}

### 2020-07-23 tex/background.tex

@@
 
+Verification and validation of computational models---often abbreviated V\&V and viewed in concert---has developed into a mature subject with more than two decades of organized efforts to standardize it, dedicated conferences, and a  journal.
+The American Society of Mechanical Engineers (ASME), a standards-developing organization, formed its first Verification and Validation committee (known as V\&V 10) in 2001, with the charter: 
+``to develop standards for assessing the correctness and credibility of modeling and simulation in computational solid mechanics.''
+It approved its first document in 2006: The Guide for Verification and Validation in Computational Solid Mechanics (known as V\&V 10-2006). 
+The fact that this guide was five years in the making illustrates just how complex the subject matter, and building consensus about it, can be. 
+Since that first effort, six additional standards sub-committees have tackled V\&V in a variety of contexts. 
+V\&V 70 is the latest, focused on machine-learning models.
+The key principles laid out in the first V\&V standard persevere through the many subsequent efforts that have operated to this day. 
+They are:
+
+\begin{enumerate}
+
+\item[$\triangleright$] Verification must precede validation.
+\item[$\triangleright$] The need for validation experiments and the associated accuracy requirements for computational model predictions are based on the intended use of the model.
+\item[$\triangleright$] Validation of a complex system should be pursued in a hierarchical fashion from the component level to the system level.
+\item[$\triangleright$] Validation is specific to a particular computational model for a particular intended use.
+\item[$\triangleright$] Validation must assess the predictive capability of the model in the physical realm of interest, and it
+must address uncertainties that arise from both simulation results and experimental data.
+
+\end{enumerate}
+
+The process of \emph{verification} establishes that a computational model correctly describes the intended mathematical equations and their solutions.
+It encompasses both code correctness, and solution accuracy.
+\emph{Validation}, on the other hand, seeks to determine to which measure a computational model represents the physical world. 
+We like to say that ``verification is solving the equations right, and validation is solving the right equations'' (source unknown). 
+But in reality the exercise can be much more complicated than this sounds. 
+Computational models in most cases are built in a hierarchy of simplifications and approximations, and comparing with the physical world means conducting experiments, which themselves carry uncertainties.
+As we will discuss in this paper, verification and validation in contexts that involve complex physics at less tractable scales (either very small, or very large), or where experimental methods are nascent, proceeds in a tangle of researcher judgements and path finding.
+
 \subsection{Description of the PyGBe software}

### 2020-07-23 tex/background.tex

@@
 
+\medskip
+
+Reproducibility and replication (we could call it R\&R), on the other hand, preoccupy scientific communities more recently. 
+Agreement on the terminology, to begin with, has been elusive \cite{barba2018}. 
+The National Academies of Science, Engineering and Medicine (NASEM) released in May 2019 a consensus study report on Replicability and Reproducibility in Science \cite{NASEM2019} with definitions as follows.
+``Reproducibility is obtaining consistent results using the same input data, computational steps, methods, and code, and conditions of analysis.
+Replicability is obtaining consistent measurements or results, or drawing consistent conclusions using new data, methods, or conditions, in a study aimed at the same scientific question.''
+According to these definitions, reproducibility demands full transparency of the computational workflow, which at the very least means open code and open data?where `open` means shared at time of publication (or earlier) under a standard public license.
+This condition is hardly common: among the few systematic efforts to assess the state of reproducibility that have been made, more than half of surveyed works cannot be reproduced, mainly due to missing digital artifacts.
+
 \subsection{Description of the PyGBe software}

### 2020-07-23 tex/results.tex
Finish draft on rockstuhl
fix reference name

@@
 Due to the nature of the geometry, and its sharp edges it was challenging to see proper convergence. However,
-for this type of physics, convergence has been studied in our previous work \cite{ClementiCooperBarba2019}. 
+for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. 
 In the Figure \ref{fig:cube535} we show a grid independence study, where we go from a mesh of 15552 
@@
             We present the results for normal incidence and 22 degrees incidence, 
-            for different aspect ratios (AR)
-            }
+            for different aspect ratios (AR)}
     \label{fig:AR_22_vs_norm}

### 2020-07-24 tex/results.tex
Add more context into ellis replication

@@
 
-There are two results from this paper that we aim to replicate, and one of them is a comparison
-against experimental results which will lead to a validation.
+ %%% Ellis work summary %%%%
+The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
+resonant modes in localized surface phonon-polariton nanostructures. They study the
+excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
+polarized reflectance measurements on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
+width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
+($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
+to reduce coupling. In their simulations and experiments they excite the localized SPhP
+resonances, they perform polarized reflectance measurements with the incident polarization 
+oriented parallel or perpendicular to the long axis of the pillars.  
+ %%% Ellis work summary %%%%
 
-The first result we show is a replication of a result presented in their supplementary 
-material FigureS4 {\color{red}(note sure how to cite this, maybe a link)}. We aimed to replicate the 
-black curve since the simulation setup is possible to replicate using PyGBe. For each aspect ratio (AR) 
+We aim to replicate the computational result presented in Figure S4 of their supplementary 
+material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
+figure they show simulation results for the resonance spectral position of the lower frequency 
+mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
+We first attempted to replicate this result since they have simulations with the gap between pillars 
+is 5000 nm, and this cause negligible coupling. This result is suitable to compare with 
+what we can model using \pygbe.
+
+\textbf{Difference between methods, mesh and dielectric data}
+
+\textit{methods}
+In Ellis et al simulations they solve full Maxwell equations via the RF package of the finite
+element method software COMSOL. To represent the array of pillars and their interactions, they use
+periodic boundary conditions of one pillar over a portion of substrate. They present the reflectance 
+as a function of the wave number. As we mentioned before, we use the boundary element method in 
+the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
+compared to the wavelength involved in the simulations (800-1000 cm$^-1$). We measure extinction cross 
+section, which will express as peaks instead of inverted peaks (as in reflection) since you see maximum
+extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
+looking to match the wave number at which these events happen.
+
+\textit{mesh}
+For the case of aspect ratio AR=4 we count with a triangular surface mesh provided by the authors of 
+Ellis et al. Which is a non-structured mesh of approximately 4 thousand elements. To produce the remaining 
+meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
+After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
+uniform mesh, we needed to double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
+I'M NOT SURE IF WE WANT TO PUT THEM, SINCE WE DON'T HAVE SPACE).
+To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
+replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.
+
+\textit{dielectric data}
+The dielectric data for the simulations, was given by the authors of the paper via a private communication.
+
+To be able to replicate this results, we need to identify the lower frequency mode for each of
+the aspect ratios in our computations. For each aspect ratio (AR) 
 value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
-800-1000 $cm^{-1}$, we identify the the lower frequency mode ($E_{100}$ in Ellis paper)  that is not a 
-longitudinal mode. We identify the Longitudinal modes by comparing normal vs 22 deg incidence runs. These
-modes due to its nature do not show up in the normal incidence runs. Then, on the 22 deg incidence 
-computations we choose the lower wave number mode that it's not a longitudinal mode. The simulations were 
-performed for the Long Edge orientation, meaning that the electric field is polarized along the long edge 
-of the pillar that is not the height.
+800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper)  that is not a 
+longitudinal mode (mode related to the hight of the pillar, only visible when the incidence of the 
+electric field is not normal). We can identify the longitudinal modes by comparing normal vs 22 degrees 
+angle of incidence runs. As we mentioned the longitudinal modes, due to its nature, do not appear when we 
+have the normal incidence . Then, on the 22 degree incidence computations we choose the lower wave number mode
+that it's not a longitudinal mode.
+
+Figure \ref{fig:AR_22_vs_norm} show the results of the extinction cross section of a SiC pillar of fixed
+height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm). The simulations where performed 
+performed for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
+when having normal incidence. (I SHOULD PROBABLY MAKE A DIAGRAM OF THIS)
+
+In Figure \ref{fig:AR_22_vs_norm} and Table \ref{tab:ar_peaks} we show the resonance peaks and
+their corresponding wavelengths. In the table we mark in bold the peaks which correspond to 
+the $E^{\parallel}_{100}$ mode.
 
@@
     \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
-    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
-             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
-            Normalized by maximum extinction cross section as a function of wave number,
-            for a pillar orientation such that the electric field is parallel polarized 
-            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
-            We present the results for normal incidence and 22 degrees incidence, 
-            for different aspect ratios (AR)}
+    \caption{Extinction cross section across wave number for SiC pillars of multiple aspect ratios,  
+             (H=950 nm, W=400nm, L=400-2800 nm (AR=1-7)), where we have normal incidence and a 
+             22 degrees incidence.
+            }
     \label{fig:AR_22_vs_norm}
@@
       field is parallel to the length (L) of the pillar. We have normal incidence and 22 degrees.}
-      \label{tab:table1}
+      \label{tab:ar_peaks}
       \begin{tabular}{c c c c c c c c}
@@
         \hline
-
       \end{tabular}
@@
 
-In other words, we choose the lower mode (lower wavenumber) from the normal 
-incidence cases.
-
-Our simulations differ on the method and we do not have a substrate included. The black curve on 
-Ellis et al \cite{ellis2016} represents the resonance positions for the $E_{100}$ mode for the different 
-aspect ratios when the pillar are separated by a 5000 nm gap. The simulations performed with \pygbe 
-consist of one isolated pillar.
+Once we identify the proper modes, we proceed to the replication of Figure S4 on the 
+supplementary material of Ellis et al work. It is worth mentioning that we limit ourselves to
+the replication of the black curve in their plot, since in this case the pillars are separated 
+by 5000 nm which means the coupling effects are negligible. Figure \ref{fig:rep_FS4_ellis} shows
+the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
+with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
+the cases
 
@@
     \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
-    \caption{Replication of figure S4 of supplementary material of Ellis 2016}
+    \caption{Replication of figure S4 of supplementary material of Ellis 2016. Wave
+    number at which happens the $E^{\parallel}_{100}$ mode for different aspect ratios.}
     \label{fig:rep_FS4_ellis}
@@
 
- If we calculate de relative percentage error for each of these points we get:
-
  \begin{table}
     \centering
-    \caption{\label{table:err_AR} Percentage error for different aspect ratios.} 
+    \label{tab:err_AR}
+    \caption{Percentage error for different aspect ratios.} 
     \begin{tabular}{c c}

### 2020-07-24 tex/results.tex
Add ellis results explanation

@@
     \centering
+    \caption{Percentage error for different aspect ratios.} 
     \label{tab:err_AR}
-    \caption{Percentage error for different aspect ratios.} 
     \begin{tabular}{c c}
     \hline%\toprule
-    ARR & \% error \\
+    AR & \% error \\
     \hline%\midrule
@@
 
-\pygbe AR=4 attempt of validation Figure 2a (see Figure \ref{fig:pygbe_vs_exp_2a})
+\subsubsection{Validation of \pygbe against Fig 2a experimental results}
+
+For the case of aspect ratio four (AR=4) we obtain the smallest error using the uniform
+mesh. Since we count with the mesh provided by the authors, and knowing that our computation 
+for the mode $E^{\parallel}_{100}$ compares well with their computations, we attempted to 
+validate our simulations with their experimental results (red curve on paper), as well 
+as to replicate their simulations (green curve on paper) on Figure 2a of their paper.
+Figure 2a of Ellis et al, presents measured and simulated reflectance of SiC pillar
+arrays with a 500 nm gap. All their measurements and simulations were performed with 
+22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
+elongated size of the pillar.
+
+Using \pygbe we compute the extinction cross section of an isolated SiC pillar (AR=4)
+with no substrate, submerged in air under a constant electric field in the z-direction, 
+and rotate the orientation of the pillar to match the angle of incidence. 
+(SHOULD PROBABLY PUT A DIAGRAM OF THIS). In Figure \ref{fig:pygbe_vs_exp_2a} we present 
+comparison of our simulations and the experimental results from Ellis et al. There is a 
+difference in the peaks wavelength that is noticeable. This could be attributed to the
+fact that in their experiments the separation between pillars is of 500 nm, which implies
+there are coupling effects that in our simulations are not contemplated.
 
@@
     \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
-    \caption{\pygbe vs experiments, figure 2a of Ellis 2016. Ellis et al 
-    has near field interaction in its experiments. Ellis data was digitized
-    with web digitizer.}
+    \caption{\pygbe vs experiments of figure 2a of Ellis 2016. Ellis data 
+    was digitized with web digitizer.}
     \label{fig:pygbe_vs_exp_2a}
@@
 
-First order approximation to achieve validation. In our code we do not have near 
-field interaction. From Figure S4 in supplementary material of Ellis et al. We know that 
-for the first mode ($E_{100}$) the difference between interaction and no interaction is 
-12.17 $cm^{-1}$ (obtained from digitized data). If we use this as a first order approximation,
-we can subtract that value from our curve, and the results are in Figure \ref{fig:val_2a}
+\paragraph{First order correction}
+
+Since our simulations do not count for coupling effects, we can not strictly imitate 
+the conditions to validate our solver. However, from Figure S4 on the supplementary 
+material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
+mode by a shift of 12.17 cm$^-1$. Therefore as a \textit{first order correction} we can 
+subtract this value from our simulations, to contemplate for coupling effects. In Figure 
+\ref{fig:val_2a} we present the result after applying the correction for coupling effects.
 

### 2020-07-24 tex/background.tex
a bit more on V&V and UQ

@@
 Computational models in most cases are built in a hierarchy of simplifications and approximations, and comparing with the physical world means conducting experiments, which themselves carry uncertainties.
+
 As we will discuss in this paper, verification and validation in contexts that involve complex physics at less tractable scales (either very small, or very large), or where experimental methods are nascent, proceeds in a tangle of researcher judgements and path finding.
+In practice, validation activities reported in the scholarly literature often concentrate on using a stylized benchmark, and comparing experimental measurements with the results from computational models on that benchmark.
+Seldom do these activities address the key principles of pursuing validation in a hierarchical fashion from the component to the system level, and of assessing the predictive capability of the computational model accounting for various sources of uncertainties.
+Comprehensive validation studies are difficult, expensive, and time consuming. 
+Often, they are severely limited by practical constraints, and the conclusions equivocal. 
+Yet the computational models still provide useful insights into the research or engineering question at hand, and we build trust on them little by little.
 
-\medskip
+Verification and validation align on one axis of the multi-dimensional question of when are claims to knowledge arising from modeling and simulation justified, credible, true \cite{winsberg-2010}.
+Two other axes of this question are: reproducibility and replication, and uncertainty quantification (UQ).
+Uncertainty quantification uses statistical methods to give objective confidence levels for the results of simulations. 
+Uncertainties typically stem from input data, modeling errors, genuine physical uncertainties, random processes, and so on. 
+A scientific study may be reproducible, the simulations within it undergone V\&V, yet the results are still uncertain. 
+Building confidence in scientific findings obtained through computational modeling and simulation entails efforts in the three ``axes of truth'' described here.
 
-Reproducibility and replication (we could call it R\&R), on the other hand, preoccupy scientific communities more recently. 
+Reproducibility and replication (we could call it R\&R) preoccupy scientific communities more recently. 
 Agreement on the terminology, to begin with, has been elusive \cite{barba2018}. 
@@
 Replicability is obtaining consistent measurements or results, or drawing consistent conclusions using new data, methods, or conditions, in a study aimed at the same scientific question.''
-According to these definitions, reproducibility demands full transparency of the computational workflow, which at the very least means open code and open data?where `open` means shared at time of publication (or earlier) under a standard public license.
+According to these definitions, reproducibility demands full transparency of the computational workflow, which at the very least means open code and open data, where `open` means shared at time of publication (or earlier) under a standard public license.
 This condition is hardly common: among the few systematic efforts to assess the state of reproducibility that have been made, more than half of surveyed works cannot be reproduced, mainly due to missing digital artifacts.

### 2020-07-24 tex/background.tex
add more on R&R

@@
 According to these definitions, reproducibility demands full transparency of the computational workflow, which at the very least means open code and open data, where `open` means shared at time of publication (or earlier) under a standard public license.
-This condition is hardly common: among the few systematic efforts to assess the state of reproducibility that have been made, more than half of surveyed works cannot be reproduced, mainly due to missing digital artifacts.
+This condition is infrequently satisfied.
+The NASEM report describes how a number of systematic efforts to reproduce computational results have failed in more than half of the attempts made, mainly due to insufficient detail on digital artifacts, such as data, code and computational workflow \cite{moraila-etal-2014,iqbal-etal-2016,chang-li2018,stodden-etal-2018}.
+Recommendation 4-1 of the NASEM report states that 
+``to help ensure reproducibility of computational results, researchers should convey clear, specific, and complete information about any computational methods and data products that support their published results in order to enable other researchers to repeat the analysis, unless such information is restricted by nonpublic data policies.
+That information should include the data, study methods, and computational environment'' \cite{NASEM2019}.
+
+Although it may seem evident that running an analysis with identical inputs would result in identical outputs, this is sometimes not true. 
+For example, the combination of floating-point representation of numbers and parallel processing means that running the same software with the same input data may give different numerical results. 
+In some research settings, it may make sense to relax the requirement of bitwise reproducibility and settle on reproducible results within an accepted range of variation (or uncertainty). 
+This can only be decided, however, after fully understanding the numerical-analysis issues affecting the outcomes---and the risk associated with an uncertainty range. 
+Researchers using high-performance computing thus recognize that when different runs with the same input data produce slightly different numeric outputs, each of these results is equally credible, and the output must be understood as an approximation to the correct value within a certain accepted uncertainty.
+
+Beyond the particulars of high-performance or parallel computing, what makes reproducibility so difficult to achieve? 
+A number of factors can contribute to the lack of reproducibility in research. 
+In addition to lack of access to non-public data and code, the NASEM report lists the following contributors to lack of reproducibility:
+
+\begin{enumerate}
+
+\item[$\triangleright$] Inadequate record-keeping: the original researchers did not properly record the relevant digital artifacts such as protocols or steps followed to obtain the results, the details of the computational environment and software dependencies, and/or information on the archival of all necessary data.
+\item[$\triangleright$]  Non-transparent reporting: the original researchers did not transparently report and provide open access to or archive the relevant digital artifacts necessary for reproducibility.
+\item[$\triangleright$]  Obsolescence of the digital artifacts: over time, the digital artifacts in the research compendium are compromised because of technological breakdown and evolution or lack of continued curation.
+\item[$\triangleright$]  Flawed attempts to reproduce others' research: the researchers who attempted to reproduce the work lacked expertise or failed to correctly follow the research protocols.
+\item[$\triangleright$]  Barriers in the culture of research: lack of resources and incentives to adopt computationally reproducible and transparent research across fields and researchers.
+
+\end{enumerate}
+
+Improving computational reproducibility hinges on capturing and sharing information about the computational environment and steps required to collect, process, and analyze data.
+Scientific workflows represent a complex flow of data products through various steps of collection, transformation, and analysis to produce an interpretable result. 
+Capturing provenance of the result is increasingly difficult to do using manual processes. 
+Thus, to support computational reproducibility, efforts have been under way for several years to develop workflow-management systems that capture and store data and workflow provenance automatically. 
+With such systems, results can be reliably linked to the computational process that derived them, and computational tasks can be automated, allowing them to be rerun and shared.
+With regards to software management, version-control systems are used to automatically capture the history of all changes made to the source code of a computer program. 
+This creates a history of changes and allows the developers to better understand the code and to identify possible problems or errors.
+Recently, the concept of version control has been extended to data files. 
+These files are generally too large to be stored in standard version-control systems, and they are often in a binary format that cannot be versioned. 
+Rather, data version control excludes the large data files from the main versioned repository, automatically collects data provenance, records data processing steps into a (reproducible) pipeline, and connects with cloud services where large data files are stored.
+Recent technological advances in version control, virtualization, computational notebooks, and automatic provenance tracking have the potential to simplify reproducibility, and tools have been developed that leverage these technologies.
+Still many questions remain answered both to understand the gaps left by existing tools and to develop principled approaches that fill those gaps.
 

### 2020-07-24 tex/background.tex
start subsection on pygbe

@@
 
+Our research group has been developing PyGBe---pronounced \emph{pigb\={e}}---for several years. 
+It was first written for biomolecular-electrostatics calculations using a continuum model of proteins in water or an ionic solution. 
+The solution method applies a boundary integral approximation of the governing Poisson-Boltzmann or Poisson equations, to obtain electrostatic field and potential on the molecular surface. 
+In the implicit-solvent model, this information is used to compute the quantity of interest: solvation energy, which is diagnostic for questions of protein binding affinity, protein-surface interactions, and others.
+PyGBe uses a fast-summation algorithm via a Barnes-Hut treecode \cite{BarnesHut1986}, and accelerates the computationally intensive parts of the code on NVIDIA GPU hardware using CUDA kernels in the treecode, interfacing with PyCUDA \cite{klockner2012pycuda}.
+Other portions of the code are written in C$++$, wrapped using \texttt{swig}, to extract more performance \cite{CooperETal2016}.
+
 \subsection{Physics context for this work}

### 2020-07-24 tex/results.tex
fix mising sentence
resize figure to stop warning
made a comment on extra peaks

@@
 presents the scattering cross section of a SiC rectangular cylinder for three different object 
-sizes. To comply with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
-case where a=672 nm and b=328 nm.
+sizes. To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
+dimension of the geometry) we chose the particular case where a=672 nm and b=328 nm.
 
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
+    \includegraphics[width=0.8\textwidth]{AR_22_vs_norm.pdf} 
     \caption{Extinction cross section across wave number for SiC pillars of multiple aspect ratios,  
@@
 \ref{fig:val_2a} we present the result after applying the correction for coupling effects.
+It is worth mentioning that the far left (837 cm$^-1$) and far right (964 cm$^-1$) peaks 
+on Ellis results, are peaks associated with zone-folded LO (longitudinal) phonons, in 
+particular P1 (837 cm$^-1$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
+do not discuss this result into detail, but they concentrate their analysis on the peaks
+that happen between 864–961 cm$^-1$
 

### 2020-07-24 tex/background.tex
Add phyiscs context, needs work

@@
 \subsection{Physics context for this work}
+
+In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
+mid to long wave infrared. Nanostructures of these materials show figure of merits that exceed that are not possible using plasmonic metals. This effect is due to the properties 
+of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 
+be observed in metals like silver in the blue part of the wavelength spectrum. 
+In plasmonics, when we illuminate a small particle made of metallic materials we will observe that certain wavelengths will excite a surface plasmon, which is the result of 
+the oscillation of free electrons. The main difference with polar dielectrics like SiC is that for this material, is that the frequency of the incoming light matches instead the
+resonance frequency of the Si and C sublattices \cite{caldwell2015,rockstuhl2005}. This excitation leads to a strong extinction cross section at the resonance wavelength, and an 
+enhanced near field amplitude. These behavior can be model  with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
+of the nanoparticle, we can still applied the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.
+
+When studying both Phonon Polaritons and Plasmons resonances, we can analyze the spectrums by measuring different quantities. We can measure scattering cross section, extinction cross section 
+(scattering plus absorption), as well as reflection. These different approaches are comparable since the \textit{variable of interest} is the wavelength/frequency at which 
+the resonance modes happen. Whether we measure reflection or extinction cross section, the wavelength/frequency at which the peaks happen remains the same. Along the course of this 
+work we will concentrate on study the wavelength/frequency at which the resonance modes happen and we will aim to replicate results from Rockstuhl et al. 2005 \cite{rockstuhl2005} and 
+from Ellis et al. 2016 \cite{ellis2016}, and we will validate our software against experimental results from Ellis et al. 2016 \cite{ellis2016}.

### 2020-07-24 tex/background.tex
fix typo
typo

@@
 In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
-mid to long wave infrared. Nanostructures of these materials show figure of merits that exceed that are not possible using plasmonic metals. This effect is due to the properties 
+mid to long wave infrared. Nanostructures of these materials show figure of merits that are not possible using plasmonic metals. This effect is due to the properties 
 of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 
@@
 
-When studying both Phonon Polaritons and Plasmons resonances, we can analyze the spectrums by measuring different quantities. We can measure scattering cross section, extinction cross section 
+When studying both Surface Phonon Polaritons and Surface Plasmons resonances, we can analyze the spectrums by measuring different quantities.
+We can measure scattering cross section, extinction cross section
 (scattering plus absorption), as well as reflection. These different approaches are comparable since the \textit{variable of interest} is the wavelength/frequency at which 

### 2020-07-24 tex/results.tex
reference to ellis ang of inc figure

@@
 electric field is not normal). We can identify the longitudinal modes by comparing normal vs 22 degrees 
-angle of incidence runs. As we mentioned the longitudinal modes, due to its nature, do not appear when we 
+angle of incidence runs (see Figure \ref{fig:ellis_ang_inc}). As we mentioned the longitudinal modes, due to its nature, do not appear when we 
 have the normal incidence . Then, on the 22 degree incidence computations we choose the lower wave number mode
 that it's not a longitudinal mode.
+
+Note: Ellis et al., changes the angle of incidence of the illuminating vector while in \pygbe we achieve this by
+rotating the geometry instead.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{ellis_ang_inc.pdf} 
+    \caption{Diagram of angles of incidence in \pygbe setup to comply with Ellis et al. disposition.}
+    \label{fig:ellis_ang_inc}
+ \end{figure}
 
@@
 with no substrate, submerged in air under a constant electric field in the z-direction, 
-and rotate the orientation of the pillar to match the angle of incidence. 
-(SHOULD PROBABLY PUT A DIAGRAM OF THIS). In Figure \ref{fig:pygbe_vs_exp_2a} we present 
+and rotate the orientation of the pillar to match the angle of incidence (see Figure \ref{fig:ellis_ang_inc}).
+In Figure \ref{fig:pygbe_vs_exp_2a} we present 
 comparison of our simulations and the experimental results from Ellis et al. There is a 

### 2020-07-24 tex/background.tex
more on pygbe-lspr

@@
 Our research group has been developing PyGBe---pronounced \emph{pigb\={e}}---for several years. 
-It was first written for biomolecular-electrostatics calculations using a continuum model of proteins in water or an ionic solution. 
-The solution method applies a boundary integral approximation of the governing Poisson-Boltzmann or Poisson equations, to obtain electrostatic field and potential on the molecular surface. 
+It was first written for biomolecular-electrostatics calculations using a continuum model of proteins in water or an ionic solvent. 
+The computational model applies a boundary integral form of the governing Poisson-Boltzmann and Poisson equations, to obtain the electrostatic field and potential on the molecular surface. 
 In the implicit-solvent model, this information is used to compute the quantity of interest: solvation energy, which is diagnostic for questions of protein binding affinity, protein-surface interactions, and others.
-PyGBe uses a fast-summation algorithm via a Barnes-Hut treecode \cite{BarnesHut1986}, and accelerates the computationally intensive parts of the code on NVIDIA GPU hardware using CUDA kernels in the treecode, interfacing with PyCUDA \cite{klockner2012pycuda}.
+Biomolecules are modeled as dielectric cavities inside an infinite continuum solvent, and the partial differential equations are solved via a boundary element method, leading to a dense linear system of equations.
+PyGBe uses a fast-summation algorithm via a Barnes-Hut treecode \cite{BarnesHut1986}, and accelerates the computationally intensive parts of the code on Nvidia GPU hardware using CUDA kernels in the treecode, interfacing with PyCUDA \cite{klockner2012pycuda}.
 Other portions of the code are written in C$++$, wrapped using \texttt{swig}, to extract more performance \cite{CooperETal2016}. 
+These features allow PyGBe to handle problems with half a million boundary elements or more.
+
+In more recent work, we expanded the capabilities of PyGBE to applications of computational nanoplasmonics for biosensing \cite{ClementiETal2019}. 
+Applying the long-wavelength limit, one can model the phenomenon of localized surface plasmon resonance (LSPR) via electrostatics, instead of the full Maxwell equations. 
+This phenomenon is harnessed in nanosensors for detecting with high sensitivity the presence of biomolecules through shifts in resonance frequency. 
+In LSPR, an electromagnetic wave excites the free electrons on the surface of a metallic nanoparticle. 
+The name given to these electron-cloud vibrations is plasmons. 
+In this setting, they resonate with the incoming field, and the energy is either absorbed by the nanoparticle or scattered in all directions, causing what's called extinction.
+Since the resonance frequency depends on the dielectric environment, the change produced by a biomolecule approaching the metallic nanoparticle results in a frequency shift, and a means of detecting its presence.
+The electrostatic approximation allows using the methods implemented in PyGBe, after substantial code development to permit using complex-valued permittivities, and to incorporate an external electric field into the model.
+These changes included re-writing the Krylov iterative solver to work with complex numbers, and splitting the treecode evaluation into real and imaginary parts. 
+New functions were added to read from configuration files the data describing the electric field, to compute the dipole moment, and to compute the final quantity of interest: extinction cross-section.
+We reported a major new release of the software in 2017 \cite{ClementiETal2017}.
 
@@
 In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
-mid to long wave infrared. Nanostructures of these materials show figure of merits that are not possible using plasmonic metals. This effect is due to the properties 
+mid to long wave infrared. Nanostructures of these materials show figure of merits that exceed that are not possible using plasmonic metals. This effect is due to the properties 
 of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 

### 2020-07-24 tex/results.tex

@@
 %%% Rockstuhl work summary%%%%
-The work of Rockstuhl et al.\cite{rockstuhl2005} study the phonon-polariton response of silicon carbide (SiC)
+The work of Rockstuhl et al.\cite{rockstuhl2005} studies the phonon-polariton response of silicon carbide (SiC)
 nanoparticles using the boundary element method. They analyze different "cylindrical particles"
-made of 6H-SiC as a function of geometrical cross section. These "cylinders" have an infinite
-extension in the third dimension, and they solve these geometries numerically with a 2D 
-boundary element method from their previous work \cite{rockstuhl2003}. 
+made of 6H-SiC as a function of geometrical cross section.They use a 2D boundary element method 
+previously developed by the group \cite{rockstuhl2003}, where they extend third dimension to infinity
+(hence the name cylinder).
 %%% Rockstuhl work summary%%%%
 
-We decided to replicate one of the results that they present on Fig.14 of their paper, which 
-presents the scattering cross section of a SiC rectangular cylinder for three different object 
-sizes. To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
+We decided to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}, which 
+presents the scattering cross section of a SiC rectangular cylinder for three different aspect ratios. 
+To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
 dimension of the geometry) we chose the particular case where a=672 nm and b=328 nm.
@@
 mode by a shift of 12.17 cm$^-1$. Therefore as a \textit{first order correction} we can 
-subtract this value from our simulations, to contemplate for coupling effects. In Figure 
+subtract this value from our simulations to count for coupling effects. In Figure 
 \ref{fig:val_2a} we present the result after applying the correction for coupling effects.

### 2020-07-24 tex/background.tex
last bit on pygbe verification

@@
 New functions were added to read from configuration files the data describing the electric field, to compute the dipole moment, and to compute the final quantity of interest: extinction cross-section.
-We reported a major new release of the software in 2017 \cite{ClementiETal2017}.
+We reported a major new release of the software in 2017 \cite{ClementiETal2017}, and later  presented the mathematical formulation for electromagnetic scattering in the long-wavelength setting and its associated continuum and discretized integral equations, and results including verification activities and a sensitivity calculations on a biosensor model \cite{ClementiETal2019}.
+For verification, we conducted grid-convergence studies in two settings.
+In the first, we set up a computational model for a spherical silver nanoparticle in a constant electric field, leading to an analytical solution for the extinction cross-section. 
+The second case does not have a closed form solution: a spherical nanoparticle with a nearby protein (analyte), under an electric field. 
+To estimate relative errors in the extinction cross-section, in this case, we made use of the method of Richardson extrapolation.
+These verification activities build our confidence on the computational model---moreover, our work was published following careful reproducibility practices, including the release of reproducibility packages for all results.
+Nevertheless, the gold standard of confidence in the predictive capability of the model comes from validation: hunting for an opportunity to conduct validation studies with PyGBe in these settings led us through the twisted path that we report in this paper.
 

### 2020-07-25 tex/background.tex
fix typo

@@
 resonance frequency of the Si and C sublattices \cite{caldwell2015,rockstuhl2005}. This excitation leads to a strong extinction cross section at the resonance wavelength, and an 
-enhanced near field amplitude. These behavior can be model  with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
+enhanced near field amplitude. These behaviors can be model with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
 of the nanoparticle, we can still applied the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.

### 2020-07-25 tex/results.tex
polish upto grid independence

@@
 
-\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem, 
-while we solve a 3D model. In our case the geometry has a finite third dimension. To cope with this
-we will extend the third direction considerably, and study this effect.
-We compute extinction cross section (scattering plus absorption) while Rockstuhl work present only scattering. 
-But since in both scattering and absorption the resonance occur at the same wavelengths, the results are 
-comparable.
+\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem of 
+full Maxwell equations, while we solve a 3D problem with the electrostatic approximation . 
+We do not count with information on their code implementations, discretization schemes, or solver.  
+We compute extinction cross section (scattering plus absorption) while Rockstuhl work present only scattering
+cross section. But since  the variable of interest is the wavelength at which the resonance modes occur, the 
+results are comparable.
 
-\textit{mesh}: Their work does not provide any details regarding the discretization of their geometries or 
-parameters involved in the simulations. We performed a grid independence study to make sure that we are
-solving properly the physics and minimizing errors due to discretization.
+\textit{mesh}: Their work does not provide any details regarding the discretization of the geometries or 
+parameters involved in the simulations.
+We performed a grid independence study to make sure that we are solving properly the equations and 
+minimizing errors due to discretization. Rockstuhl has a 2D geometry (infinite third dimension) while we deal 
+with a 3D representation of the geometry.
 
-\textit{dielectric data}: The use 6H-SiC as material, and they obtained their data from a a source that we
+\textit{dielectric data}: They use 6H-SiC as material, and they obtained their data from a a source that we
 were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
-via private communications.
+via private communications from the authors of Ellis et al \cite{ellis2016}.
 
@@
 We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
-constant electric field aligned with the z-axis.
-(similar to quadratic cylinder on Fig 18 of Rockstuhl et.al). 
-Due to the nature of the geometry, and its sharp edges it was challenging to see proper convergence. However,
-for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. 
-In the Figure \ref{fig:cube535} we show a grid independence study, where we go from a mesh of 15552 
+constant electric field aligned with the z-axis (similar setup to quadratic cylinder on Fig 18 of 
+Rockstuhl et.al)\cite{rockstuhl2005}. 
+Due to the nature of the geometry and its sharp edges it was challenging to see proper convergence. However,
+for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
+Figure \ref{fig:cube535} shows the grid independence study where we go from a mesh of 15552 
 triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
-triangles and the computed results do not change.
+triangles, and the computed results do not change.
 
@@
 
-It is worth noting that the extinction cross section curve in Figure \ref{fig:cube535} has extra peaks, 
+It is worth noting that the extinction cross section curve in Figure \ref{fig:cube535} has extra peaks 
 compared to the results of Figure 18 on Rockstuhl, this is due to the 3D nature of our case and the sharp 
-edges. This will be approach in the following results where we attempt a replication of one of teh results 
-of Figure 14 of Rockstuhl work.
+edges, being the latest an effect also mentioned in Rockstuhl et al. results. The 3D effect will be approach
+in the following results where we attempt a replication of one of teh results of Figure 14 of Rockstuhl work.
 
@@
 performed for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
-when having normal incidence. (I SHOULD PROBABLY MAKE A DIAGRAM OF THIS)
+when having normal incidence (see Figure \ref{fig:ellis_ang_inc}).
 

### 2020-07-25 tex/results.tex
try to declutter Rockstuhl section

@@
 We chose to replicate the result of Rocksuthl et al. presented in Figure 14. In particular the case where $a=672$ nm 
-and $b=328$ nmn, since these dimension comply with the requirements of the quasistatic approximation.
-They present the normalized scattering cross section of a SiC rectangular cylinder, and they perform simulation 
-for two different setups. In Rockstuhl Figure 14 (left) they have the wave vector (illumination) along the long 
-side of the geometry, which means that the electric field is parallel to the short side of the rectangle. Following, 
-a similar analysis Rockstuhl Figure 14 (right) they have the wave vector (illumination) along the short
-side of the geometry, which means that the electric field is parallel to the long side of the rectangle. These orientations,
-correspond to the images (A) and (B) in the sketch presented in Figure \ref{fig:rectangle_sketch}.
+and $b=328$ nm, since these dimension comply well with the requirements of the quasistatic approximation needed 
+to use \pygbe. In Rcokstuhl et al. work they present the normalized scattering cross section of a SiC rectangular 
+cylinder, and they perform simulation for two different setups (see Figure \ref{fig:rectangle_sketch}). In 
+Rockstuhl Figure 14 (left) they have the wave vector (illumination) along the long 
+side of the geometry, which means that the electric field is parallel to the short side of the rectangle (like in 
+Figure \ref{fig:rectangle_sketch} (B)). Following, a similar analysis Rockstuhl Figure 14 (right) they have the wave 
+vector (illumination) along the short side of the geometry, which means that the electric field is parallel to the 
+long side of the rectangle (like in Figure \ref{fig:rectangle_sketch} (A).
 
-Based on the results of the grid independence stud we decided to we used the density of the cube as a reference to 
-produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
-dimension we needed to chose a value that represents "infinity". To achieve this, we perform a study on the effects of 
-elongate the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different values of the 
-third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). 
-We see that as we extend the third dimension the intensity of some peaks decreases, this is because some
-of the peaks are related to the third dimension. Therefore, from now on we use $y=y=2688$ nm. It is worth 
-noting that we could have increased this value more, however, the simulations will become computational
-more expensive and we will still have the effects of having a 3D model.
+Based on the results of the grid independence study we decided to use the densities in the order of $6-9e^-5$
+to produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
+dimension we needed to chose a value that represents "infinity". To achieve this, we study the effects of 
+elongation on the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different
+values of the third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). We see that as we extend $y$ the 
+intensity of some peaks decreases, this is because some of the peaks are related to this component. Therefore, 
+from now on we use $y=2688$ nm. It is worth noting that we could have increased this value more, however, the
+simulations will become computational more expensive and we will still have the effects of having a 3D model.
 
@@
 
-To generate the meshes for these simulations, we used the open source software Trimesh 
+To generate the meshes for these simulations, we initially used the open source software Trimesh 
 (\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
 uniform mesh and that it was not possible to produce regular triangles with the functions 
-available. To overcome this, we created our own mesh using python scripts, and therefore 
-obtain uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
-on rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
-as a factor that will introduce extra peaks on the response. We were not able to control the 
+available when having a prism. To overcome this, we created our own mesh using python scripts,
+and create uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
+of rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
+as a factor that introduces extra peaks on the response. We were not able to control the 
 roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 

### 2020-07-25 tex/results.tex
some polishing on Ellis

@@
 excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
-polarized reflectance measurements on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
+polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
 width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
 ($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
-to reduce coupling. In their simulations and experiments they excite the localized SPhP
+to reduce coupling. In  both their simulations and experiments they excite the localized SPhP
 resonances, they perform polarized reflectance measurements with the incident polarization 
@@
 mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
-We first attempted to replicate this result since they have simulations with the gap between pillars 
-is 5000 nm, and this cause negligible coupling. This result is suitable to compare with 
+We first attempted to replicate this result since they have results where the gap between pillars 
+is 5000 nm (10 times more than in the experiments and other simulations on the paper), and 
+this diminishes the effects of coupling. This result is suitable to compare with 
 what we can model using \pygbe.
@@
 \textit{methods}
-In Ellis et al simulations they solve full Maxwell equations via the RF package of the finite
+(I DID NOT MENTION ANYTHING RELATED TO WHAT THEY DO IN THE EXPERIMENTS, SHOULD WE INCLUDE THIS?)
+
+In Ellis et al. simulations they solve full Maxwell equations via the RF package of the finite
 element method software COMSOL. To represent the array of pillars and their interactions, they use
-periodic boundary conditions of one pillar over a portion of substrate. They present the reflectance 
-as a function of the wave number. As we mentioned before, we use the boundary element method in 
+periodic boundary conditions of one pillar over a portion of substrate, and use periodic boundary conditions on it.
+They present the reflectance as a function of the wave number. 
+As we mentioned before, we use the boundary element method in 
 the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
-compared to the wavelength involved in the simulations (800-1000 cm$^-1$). We measure extinction cross 
-section, which will express as peaks instead of inverted peaks (as in reflection) since you see maximum
-extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
-looking to match the wave number at which these events happen.
+compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). We measure 
+extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots)
+since you see maximum extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
+looking to match the wave number (variable of interest) at which these events happen.
 
 \textit{mesh}
-For the case of aspect ratio AR=4 we count with a triangular surface mesh provided by the authors of 
-Ellis et al. Which is a non-structured mesh of approximately 4 thousand elements. To produce the remaining 
+For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
+Ellis et al. Which is a non-structured (HOW IS IT CALLED WHEN IS FINER WHER THERE ARE CORNERS?) mesh of
+approximately four thousand elements. To produce the remaining 
 meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
 After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
-uniform mesh, we needed to double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
-I'M NOT SURE IF WE WANT TO PUT THEM, SINCE WE DON'T HAVE SPACE).
+uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
+I'M NOT SURE IF WE WANT TO PUT THEM).
 To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
@@
 \textit{dielectric data}
-The dielectric data for the simulations, was given by the authors of the paper via a private communication.
+The dielectric data for the simulations, was given by the authors of the paper via a private communication, 
+and corresponds to experimental values of the dielectric.
 
-To be able to replicate this results, we need to identify the lower frequency mode for each of
+To be able to replicate the result of Figure S4 of the suplementary material of Ellis et al, we
+need to identify the lower frequency mode for each of
 the aspect ratios in our computations. For each aspect ratio (AR) 

### 2020-07-25 tex/background.tex
edit physics context

--- 2020-07-24 tex/background.tex
@@
 
-In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
-mid to long wave infrared. Nanostructures of these materials show figure of merits that are not possible using plasmonic metals. This effect is due to the properties 
-of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 
-be observed in metals like silver in the blue part of the wavelength spectrum. 
-In plasmonics, when we illuminate a small particle made of metallic materials we will observe that certain wavelengths will excite a surface plasmon, which is the result of 
-the oscillation of free electrons. The main difference with polar dielectrics like SiC is that for this material, is that the frequency of the incoming light matches instead the
-resonance frequency of the Si and C sublattices \cite{caldwell2015,rockstuhl2005}. This excitation leads to a strong extinction cross section at the resonance wavelength, and an 
-enhanced near field amplitude. These behavior can be model  with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
-of the nanoparticle, we can still applied the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.
+In recent years, polar dielectrics such as Silicon Carbide (SiC) have caught the attention of researchers as an alternative to plasmonic metals, 
+due to their low optical losses in in the mid- to long-wave infrared range. 
+Nanostructures made of these materials offer sensing capabilities, described by their \emph{figure of merits}, that are unattainable with plasmonic metals. 
+The figure of merits of a nanoparticle is defined as the ratio between the sensitivity and the width of the resonance peak \cite{otte-etal-2012}. 
+In turn, sensitivity is the shift in the resonance position divided by the change in the refractive index: 
+$S = \Delta \lambda / \Delta n$.
+The dielectric of these materials has a negative real part and a very small imaginary part, in the mid/long infrared region. 
+This dielectric behavior is similar to that observed in metals like silver in the blue part of the wavelength spectrum. 
+In plasmonics, when illuminating a small particle made of metallic materials, we will observe that certain wavelengths excite a surface plasmon. 
+The main difference with polar dielectrics like SiC is that for this material the frequency of the incoming light matches instead the resonance frequency of the Si and C sub-lattices \cite{caldwell2015,rockstuhl2005}.
+This excitation leads to a strong extinction cross-section at the resonance wavelength, and an enhanced near-field amplitude. 
+These behaviors can be modeled with the same approaches used for localized surface plasmon resonance, and when the wavelength is much larger than the size
+of the nanoparticle, we can again apply the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.
 
-When studying both Surface Phonon Polaritons and Surface Plasmons resonances, we can analyze the spectrums by measuring different quantities.
-We can measure scattering cross section, extinction cross section
-(scattering plus absorption), as well as reflection. These different approaches are comparable since the \textit{variable of interest} is the wavelength/frequency at which 
-the resonance modes happen. Whether we measure reflection or extinction cross section, the wavelength/frequency at which the peaks happen remains the same. Along the course of this 
-work we will concentrate on study the wavelength/frequency at which the resonance modes happen and we will aim to replicate results from Rockstuhl et al. 2005 \cite{rockstuhl2005} and 
-from Ellis et al. 2016 \cite{ellis2016}, and we will validate our software against experimental results from Ellis et al. 2016 \cite{ellis2016}.
+When studying both surface phonon polaritons and surface plasmon resonances, we can analyze the spectrums by measuring different quantities. 
+We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
+These different approaches are comparable since the \textit{quantity of interest} is the wavelength/frequency at which the resonance modes happen. 
+Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
+Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 
+and we aim to replicate results from Rockstuhl et al.\ 2005 \cite{rockstuhl2005} and from Ellis et al.\ 2016 \cite{ellis2016}, 
+and to validate our software against experimental results from Ellis et al.\ 2016 \cite{ellis2016}.

### 2020-07-25 tex/results.tex
first bunch of edits to results section

@@
 The work of Rockstuhl et al.\cite{rockstuhl2005} studies the phonon-polariton response of silicon carbide (SiC)
-nanoparticles using the boundary element method. They analyze different "cylindrical particles"
-made of 6H-SiC as a function of geometrical cross section.They use a 2D boundary element method 
-previously developed by the group \cite{rockstuhl2003}, where they extend third dimension to infinity
-(hence the name cylinder).
+nanoparticles using the boundary element method. They analyze different ``cylindrical particles''
+made of 6H-SiC, as a function of geometrical cross-section. 
+They use a two-dimensional (2D) boundary element method 
+previously developed by the group \cite{rockstuhl2003}, where they extend in the third dimension to infinity
+(hence the name ``cylinder'').
 %%% Rockstuhl work summary%%%%
 
-We decided to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}, which 
-presents the scattering cross section of a SiC rectangular cylinder for three different aspect ratios. 
+We decided to attemp to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}:
+the scattering cross-section of a SiC rectangular cylinder for three different aspect ratios. 
 To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
-dimension of the geometry) we chose the particular case where a=672 nm and b=328 nm.
+dimension of the geometry), we chose the particular case where a=672 nm and b=328 nm.
 
-\textbf{Difference between methods, mesh and dielectric data}
+\subsubsection{Differences in method, mesh and dielectric data}
 
-\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem of 
-full Maxwell equations, while we solve a 3D problem with the electrostatic approximation . 
-We do not count with information on their code implementations, discretization schemes, or solver.  
-We compute extinction cross section (scattering plus absorption) while Rockstuhl work present only scattering
-cross section. But since  the variable of interest is the wavelength at which the resonance modes occur, the 
-results are comparable.
+\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
+full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
+We lack any information about their code implementations, discretization schemes, or solver.  
+We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
+But, since the quantity of interest is the wavelength at which the resonance modes occur, the results can be compared.
 
-\textit{mesh}: Their work does not provide any details regarding the discretization of the geometries or 
+\paragraph{Mesh:} Rockstuhl et al.\ did not provide any details regarding the discretization of the geometries or 
 parameters involved in the simulations.
-We performed a grid independence study to make sure that we are solving properly the equations and 
-minimizing errors due to discretization. Rockstuhl has a 2D geometry (infinite third dimension) while we deal 
-with a 3D representation of the geometry.
+We performed a grid-independence study as a form of solution verification, and to ensure that we are 
+minimizing errors due to discretization. Rockstuhl et al.\ used a 2D geometry (infinite third dimension), while we treat the geometry in its full 3D representation.
 
-\textit{dielectric data}: They use 6H-SiC as material, and they obtained their data from a a source that we
+\paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a a source that we
 were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
-via private communications from the authors of Ellis et al \cite{ellis2016}.
+via private communications from the authors of Ellis et al.\cite{ellis2016}.
 
-\subsubsection{Grid independance study}
+\subsubsection{Grid-independence study}
 
-We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
-constant electric field aligned with the z-axis (similar setup to quadratic cylinder on Fig 18 of 
-Rockstuhl et.al)\cite{rockstuhl2005}. 
-Due to the nature of the geometry and its sharp edges it was challenging to see proper convergence. However,
+We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
+constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
+Rockstuhl et al.\cite{rockstuhl2005}). 
+Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. However,
 for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
-Figure \ref{fig:cube535} shows the grid independence study where we go from a mesh of 15552 
-triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
-triangles, and the computed results do not change.
+Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
+triangles (density $1.11\times10^-4$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^-5$ $N/\text{\AA}$) 
+triangles: the computed results show no discernible difference.
 
@@
     \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
-    \caption{Grid independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
-    electric field in the z-direction. The curves represent the extinction cross section divided by $L^2$ 
-    as a function of wavelength divided by $L$}
+    \caption{Grid-independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
+    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
+    as a function of wavelength divided by $L$.}
     \label{fig:cube535}

### 2020-07-25 tex/results.tex
minor edits, results

@@
 
-It is worth noting that the extinction cross section curve in Figure \ref{fig:cube535} has extra peaks 
-compared to the results of Figure 18 on Rockstuhl, this is due to the 3D nature of our case and the sharp 
-edges, being the latest an effect also mentioned in Rockstuhl et al. results. The 3D effect will be approach
-in the following results where we attempt a replication of one of teh results of Figure 14 of Rockstuhl work.
+It is worth noting that the extinction cross-section curve in Figure \ref{fig:cube535} has extra peaks 
+compared to the results of Figure 18 of Rockstuhl et al., due to the three-dimensional effects captured in our simulation and the sharp 
+edges, the latter effect also being mentioned by Rockstuhl et al. The 3D effects will be approached
+in the following results, where we attempt a replication of one of the results on Figure 14 of Rockstuhl et al.
 
-\subsubsection{Replication of Figure 14 (case a1) of Rockstuhl 2005}
+\subsubsection{Replication of Figure 14 (case a1) of Rockstuhl et al., 2005}
 
-We chose to replicate the result of Rocksuthl et al. presented in Figure 14. In particular the case where $a=672$ nm 
-and $b=328$ nm, since these dimension comply well with the requirements of the quasistatic approximation needed 
-to use \pygbe. In Rcokstuhl et al. work they present the normalized scattering cross section of a SiC rectangular 
-cylinder, and they perform simulation for two different setups (see Figure \ref{fig:rectangle_sketch}). In 
-Rockstuhl Figure 14 (left) they have the wave vector (illumination) along the long 
-side of the geometry, which means that the electric field is parallel to the short side of the rectangle (like in 
-Figure \ref{fig:rectangle_sketch} (B)). Following, a similar analysis Rockstuhl Figure 14 (right) they have the wave 
+We chose to replicate a result of Rocksuthl et al.\ presented in Figure 14: 
+the case where $a=672$ nm 
+and $b=328$ nm, since these dimensions are well within the limits of the quasistatic approximation 
+used in \pygbe. Rockstuhl et al.\ present the normalized scattering cross-section of a SiC rectangular 
+cylinder, and they perform simulations for two different setups, sketched in Figure \ref{fig:rectangle_sketch}. In 
+their Figure 14 (left), they have the wave vector (illumination) along the long 
+side of the geometry, which means that the electric field is parallel to the short side of the rectangle, like in 
+Figure \ref{fig:rectangle_sketch} (B). Following a similar analysis, in Figure 14 (right) of Rockstuhl et al., they have the wave 
 vector (illumination) along the short side of the geometry, which means that the electric field is parallel to the 
-long side of the rectangle (like in Figure \ref{fig:rectangle_sketch} (A).
+long side of the rectangle, like in Figure \ref{fig:rectangle_sketch} (A).
 

### 2020-07-25 tex/results.tex
more edits in results

@@
 Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
-triangles (density $1.11\times10^-4$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^-5$ $N/\text{\AA}$) 
+triangles (density $1.11\times10^{-4}$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^{-5}$ $N/\text{\AA}$) 
 triangles: the computed results show no discernible difference.
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{cubeL535nm_15Kvs19K.pdf} 
+    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
     \caption{Grid-independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
@@
 
-Based on the results of the grid independence study we decided to use the densities in the order of $6-9e^-5$
-to produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
-dimension we needed to chose a value that represents "infinity". To achieve this, we study the effects of 
-elongation on the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different
-values of the third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). We see that as we extend $y$ the 
-intensity of some peaks decreases, this is because some of the peaks are related to this component. Therefore, 
-from now on we use $y=2688$ nm. It is worth noting that we could have increased this value more, however, the
-simulations will become computational more expensive and we will still have the effects of having a 3D model.
+Based on the results of our grid-independence study, we decided to use triangle densities in the order of $6$ to $9\times10^{-5}$
+to produce the meshes for the replication of figures 14a and 14b in the work of Rockstuhl et al.\ (case $a1=672$, $b=328$). For the third 
+dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
+elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
+values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
+intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
+from now on we use $y=2688$ nm. We could have increased this value more, but the
+simulations then become computationally more expensive and we would still have the 3D effects in the model.
 
@@
     \centering
-    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14a.pdf}}
-    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14b.pdf}} 
+    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14a.pdf}}
+    \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14b.pdf}} 
     \caption{Effect of the elongation of the third direction ($y$) on the 
@@
 (\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
-uniform mesh and that it was not possible to produce regular triangles with the functions 
-available when having a prism. To overcome this, we created our own mesh using python scripts,
-and create uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
-of rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
-as a factor that introduces extra peaks on the response. We were not able to control the 
+uniform mesh and that it was not possible to obtain regular triangles with the functions 
+available when having a prism. To overcome this, we created our own mesh using Python scripts,
+and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
+of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
+as a factor that introduces extra peaks on the response. We were unable to control the 
 roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
 decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
-results on the effect of uniformity and roundness. You can see that the second peak is not
+results of the effect of uniformity and roundness. One can see that the second peak is not
 present in the green curve, which can be attributed to the effect of the roundness. This is 
-consistent with the results on Rockstuhl's work.
+consistent with the results in Rockstuhl et al.
 
@@
     \centering
-    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14a.pdf}}
-    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14b.pdf}}
+    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14a.pdf}}
+    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14b.pdf}}
     \caption{ Effect of uniformity and roundness on the mesh on the 
@@
 
-Once we have found the "best" possible geometry approximation, we show how our results 
+Once we have found the ``best'' possible geometry construction, we show how our results 
 (green curve in Figure \ref{fig:tri_reg_round_14}) compare 
@@
 the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
-presented in Figure \ref{fig:rep_14}. We can say that the main peaks presented in Rockstuhl et al. are 
-successfully replicated. While we still have the presence of a third peak in our results, we believe 
-this is a consequence of the 3D nature of our geometry.
+presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
+successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
+that this is a consequence of the 3D effects in our geometry.
 
@@
     \centering
-    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14a.pdf}}
-    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14b.pdf}} 
+    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14a.pdf}}
+    \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
     \caption{Replication of Figure 14 from Rockstuhl 2005. Extinction cross section of a

### 2020-07-25 tex/background.tex
minor fix
add roache citation

@@
 
-Verification and validation of computational models---often abbreviated V\&V and viewed in concert---has developed into a mature subject with more than two decades of organized efforts to standardize it, dedicated conferences, and a  journal.
+Verification and validation of computational models---often abbreviated V\&V and viewed in concert---have developed into a mature subject with more than two decades of organized efforts to standardize it, dedicated conferences, and a  journal.
 The American Society of Mechanical Engineers (ASME), a standards-developing organization, formed its first Verification and Validation committee (known as V\&V 10) in 2001, with the charter: 
@@
 \emph{Validation}, on the other hand, seeks to determine to which measure a computational model represents the physical world. 
-We like to say that ``verification is solving the equations right, and validation is solving the right equations'' (source unknown). 
+We like to say that ``verification is solving the equations right, and validation is solving the right equations'' \cite{roache1998}. 
 But in reality the exercise can be much more complicated than this sounds. 
@@
 We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
-These different approaches are comparable since the \textit{quantity of interest} is the wavelength/frequency at which the resonance modes happen. 
+These different approaches are comparable since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen. 
 Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 

### 2020-07-25 tex/background.tex
fix pygbe description

@@
 It was first written for biomolecular-electrostatics calculations using a continuum model of proteins in water or an ionic solvent. 
-The computational model applies a boundary integral form of the governing Poisson-Boltzmann and Poisson equations, to obtain the electrostatic field and potential on the molecular surface. 
+The computational model applies a boundary integral form of the governing Poisson-Boltzmann and Poisson equations, to obtain the electrostatic potential and its normal derivative on the molecular surface.
 In the implicit-solvent model, this information is used to compute the quantity of interest: solvation energy, which is diagnostic for questions of protein binding affinity, protein-surface interactions, and others.

### 2020-07-25 tex/background.tex
definition figure of merits

@@
 Nanostructures made of these materials offer sensing capabilities, described by their \emph{figure of merits}, that are unattainable with plasmonic metals. 
-The figure of merits of a nanoparticle is defined as the ratio between the sensitivity and the width of the resonance peak \cite{otte-etal-2012}. 
+The figure of merits of a nanoparticle is defined as the ratio between the sensitivity and the width of the resonance peak at mid-height \cite{otte-etal-2012}. 
 In turn, sensitivity is the shift in the resonance position divided by the change in the refractive index: 

### 2020-07-25 tex/results.tex
fix triangle densities

@@
 for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
-Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
-triangles (density $1.11\times10^{-4}$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^{-5}$ $N/\text{\AA}$) 
-triangles: the computed results show no discernible difference.
+Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
+ to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
+ the computed results show no discernible difference.
 

### 2020-07-25 tex/results.tex
fix bit about convergence with sharp edges

--- 2020-07-25 tex/results.tex
@@
 Rockstuhl et al.\cite{rockstuhl2005}). 
-Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. However,
-for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
-Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 
-triangles (density $1.11\times10^{-4}$ $N/\text{\AA}$) to 19,200 (density $9.05\times10^{-5}$ $N/\text{\AA}$) 
-triangles: the computed results show no discernible difference.
+Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. 
+We have completed grid-convergence analysis for this type of physics in a previous work, but using spherical geometries \cite{ClementiETal2019}. 
+With that experience, and given the difficulty caused by sharp edges, we are satisfied with studying grid-independence here instead.
+Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
+ to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
+ the computed results show no discernible difference.
 

### 2020-07-25 tex/results.tex
not really satisfied
fix part about mesh densities

@@
 
-\subsubsection{Grid-independence study}
+\subsubsection{Grid-independence study}\label{sec:independence}
 
@@
 We have completed grid-convergence analysis for this type of physics in a previous work, but using spherical geometries \cite{ClementiETal2019}. 
-With that experience, and given the difficulty caused by sharp edges, we are satisfied with studying grid-independence here instead.
+With that experience, and given the difficulty caused by sharp edges, we are content with studying grid-independence here instead.
 Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
@@
     \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
-    \caption{Grid-independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
+    \caption{Grid-independence study for a SiC cube of side $L=535$ nm submerged in air under a constant 
     electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
@@
 
-Based on the results of our grid-independence study, we decided to use triangle densities in the order of $6$ to $9\times10^{-5}$
-to produce the meshes for the replication of figures 14a and 14b in the work of Rockstuhl et al.\ (case $a1=672$, $b=328$). For the third 
-dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
+The constraints of mesh generation mean that we have only loose control on triangle density.
+Our meshes for the rectangular prism all have densities like in the coarse case of the grid-dependence study of section \ref{sec:independence}, or finer.
+For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
 elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different

### 2020-07-25 tex/results.tex
small fix

@@
 The constraints of mesh generation mean that we have only loose control on triangle density.
-Our meshes for the rectangular prism all have densities like in the coarse case of the grid-dependence study of section \ref{sec:independence}, or finer.
+Our meshes for the rectangular prism all have densities like in the coarse case of the grid-dependence study of sub-section \ref{sec:independence}, or finer.
 For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 

### 2020-07-25 tex/results.tex
typo fix

--- 2020-07-25 tex/results.tex
@@
 The constraints of mesh generation mean that we have only loose control on triangle density.
-Our meshes for the rectangular prism all have densities like in the coarse case of the grid-dependence study of section \ref{sec:independence}, or finer.
+Our meshes for the rectangular prism all have densities like in the coarse case of the grid-independence study of sub-section \ref{sec:independence}, or finer.
 For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 

### 2020-07-25 tex/results.tex
delete problematic sentence
say we share the mesh files

@@
 intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
-from now on we use $y=2688$ nm. We could have increased this value more, but the
-simulations then become computationally more expensive and we would still have the 3D effects in the model.
+from now on we use $y=2688$ nm.
 
@@
 roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
-decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
+decided to use the default settings on Trimesh. 
+(For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod})
+Figure \ref{fig:tri_reg_round_14} shows the 
 results of the effect of uniformity and roundness. One can see that the second peak is not
@@
  \end{figure}
+
+ \subsection{Reproducibility and data management} \label{sec:reprod}

### 2020-07-25 tex/results.tex
change bibstyle

--- 2020-07-25 tex/results.tex
@@
 roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
-decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
+decided to use the default settings on Trimesh. 
+For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
+Figure \ref{fig:tri_reg_round_14} shows the 
 results of the effect of uniformity and roundness. One can see that the second peak is not
@@
 (green curve in Figure \ref{fig:tri_reg_round_14}) compare 
-with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
+with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
 the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 

### 2020-07-25 tex/results.tex
start repro sub-section

@@
  \subsection{Reproducibility and data management} \label{sec:reprod}
+
+ Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
+ A key element is professional software management and engineering, and the central technology solution is version control. 
+ Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
+Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
+This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \citep{mesnard-barba2019}.
+We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.

### 2020-07-25 tex/results.tex
work on repro section

@@
  Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
+ Another key element of transparent and reproducible computational modeling is \emph{automation}.
+Automating every step means \emph{turning protocols into code.}
+For example, simulations are launched with parameters fed from a configuration file rather than an interactive prompt, and all figures and plots are produced by writing scripts, rather than pointing-and-clicking on a graphical interface.
+The goal is to create complete ``recipes'' in code, which can be run, versioned, and shared.
+
 Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
-This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \citep{mesnard-barba2019}.
+This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
 We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.

### 2020-07-25 tex/results.tex
a bit more on repro

@@
 We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
+As in our previous papers, it is possible to reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo.
+[LIST, EXPLAIN, CITE ARCHIVES] 
+\pygbe is openly developed and shared under the BSD3-clause license via its repository at \url{https://github.com/barbagroup/pygbe}.

### 2020-07-25 tex/results.tex
polish first two paragraph ellis

--- 2020-07-25 tex/results.tex
@@
 
-We decided to attemp to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}:
+We decided to attempt to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}:
 the scattering cross-section of a SiC rectangular cylinder for three different aspect ratios. 
@@
 decided to use the default settings on Trimesh. 
-For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
+(For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod})
 Figure \ref{fig:tri_reg_round_14} shows the 
@@
 (green curve in Figure \ref{fig:tri_reg_round_14}) compare 
-with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
+with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
 the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
@@
 excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
-polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
-width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
-($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
-to reduce coupling. In  both their simulations and experiments they excite the localized SPhP
-resonances, they perform polarized reflectance measurements with the incident polarization 
+and computing polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
+width ($W=400$ nm) and varied length ($L=400-4800$ nm). These pillars are patterned on a squared 
+grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments they 
+perform polarized reflectance measurements with the incident polarization 
 oriented parallel or perpendicular to the long axis of the pillars.  
@@
 
-We aim to replicate the computational result presented in Figure S4 of their supplementary 
-material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
+We first aim to replicate the computational result presented in Figure S4 of their supplementary 
+material that correspond to the black curve on their plot. In this 
 figure they show simulation results for the resonance spectral position of the lower frequency 
 mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
-We first attempted to replicate this result since they have results where the gap between pillars 
-is 5000 nm (10 times more than in the experiments and other simulations on the paper), and 
-this diminishes the effects of coupling. This result is suitable to compare with 
-what we can model using \pygbe.
+We attempted to replicate this result since the gap between the pillars 
+is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
+a good candidate to replicate using \pygbe.
 
@@
 For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
-Ellis et al. Which is a non-structured (HOW IS IT CALLED WHEN IS FINER WHER THERE ARE CORNERS?) mesh of
+Ellis et al. Which is a non-uniform mesh of
 approximately four thousand elements. To produce the remaining 
@@
  \subsection{Reproducibility and data management} \label{sec:reprod}
-
- Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
- A key element is professional software management and engineering, and the central technology solution is version control. 
- Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
-Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
-This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \citep{mesnard-barba2019}.
-We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.

### 2020-07-25 tex/results.tex
add some more edits

@@
 is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
-a good candidate to replicate using \pygbe.
+a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
+for the results presented in Figure 2a, in which they present reflectance measurements across wave number
+for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
+length of the pillars.
 
@@
 \textit{methods}
-(I DID NOT MENTION ANYTHING RELATED TO WHAT THEY DO IN THE EXPERIMENTS, SHOULD WE INCLUDE THIS?)
 
-In Ellis et al. simulations they solve full Maxwell equations via the RF package of the finite
-element method software COMSOL. To represent the array of pillars and their interactions, they use
-periodic boundary conditions of one pillar over a portion of substrate, and use periodic boundary conditions on it.
-They present the reflectance as a function of the wave number. 
-As we mentioned before, we use the boundary element method in 
-the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
-compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). We measure 
-extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots)
-since you see maximum extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
-looking to match the wave number (variable of interest) at which these events happen.
+In Ellis et al. they run experiments using reflectance spectroscopy and they compute the solution of
+Maxwell equations via the RF package of the finite element method software COMSOL. In their simulations 
+they use periodic boundary conditions of one pillar over a portion of substrate, to represent the array of 
+pillars and their interactions. 
+We use the boundary element method in the quasistatic approximation, which is suitable in these case 
+since the pillar's size is small compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). 
+We measure extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots). 
+The intensity of the peaks is not comparable, but we are looking to match the wave number (variable of interest) at which these events happen.
 

### 2020-07-26 tex/results.tex
Fix mesh description

@@
 for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
-length of the pillars.
+length of the pillars. This same case, counts with experimental results that we will use to attempt the validation of our solver.
 
@@
 \textit{mesh}
-For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
-Ellis et al. Which is a non-uniform mesh of
-approximately four thousand elements. To produce the remaining 
-meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
-After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
-uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
-I'M NOT SURE IF WE WANT TO PUT THEM).
-To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
-replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.
+
+For the case of aspect ratio $AR=4$ we count with a non-uniform triangular surface mesh (N=4398) provided by the authors of 
+Ellis et al, which we use for validation and replication of FIgure 2a of their paper. However, for the replication
+of Figure S4 of the supplementary material we needed the remaining aspect ratio meshes. We generated uniform meshes using our
+python script, and we determined the density of these meshes by comparing the extinction cross section for the case of AR=4 of 
+our mesh and the one provided by Ellis et al. We noticed that using around double the elements (N=8564) than in the original mesh and 
+rounding the edges, the relative errors for the extinction cross section where, on average, smaller than 3$\%$ and the variation on the wavelength peak
+occurrence was smaller than 1 cm$^-1$. This analysis lead us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
+the aspect ratio's variation study.
 

### 2020-07-26 tex/results.tex
pollish replication Fig s4

@@
 
-To be able to replicate the result of Figure S4 of the suplementary material of Ellis et al, we
+\subsubsection{Replication of Figure S4 of supplementary material of Ellis et al. 2016}
+
+To be able to replicate the result of Figure S4 of the supplementary material of Ellis et al, we
 need to identify the lower frequency mode for each of
@@
 800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper) that is not a 
-longitudinal mode (mode related to the hight of the pillar, only visible when the incidence of the 
-electric field is not normal). We can identify the longitudinal modes by comparing normal vs 22 degrees 
-angle of incidence runs (see Figure \ref{fig:ellis_ang_inc}). As we mentioned the longitudinal modes, due to its nature, do not appear when we 
-have the normal incidence . Then, on the 22 degree incidence computations we choose the lower wave number mode
-that it's not a longitudinal mode.
+longitudinal mode. The longitudinal mode appear only when we have an incidence angle that is off-normal, since 
+they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} show the results of the extinction 
+cross section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm), for normal 
+and 22 degrees angle of incidence. The simulations where performed 
+for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
+when having normal incidence as shown on see Figure \ref{fig:ellis_ang_inc}. From these results we select 
+the lower mode that it is not a longitudinal one and extract its wavelength (see \ref{tab:ar_peaks}) to replicate 
+\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
+with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
+the cases.
 
@@
  \end{figure}
-
-Figure \ref{fig:AR_22_vs_norm} show the results of the extinction cross section of a SiC pillar of fixed
-height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm). The simulations where performed 
-performed for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
-when having normal incidence (see Figure \ref{fig:ellis_ang_inc}).
-
-In Figure \ref{fig:AR_22_vs_norm} and Table \ref{tab:ar_peaks} we show the resonance peaks and
-their corresponding wavelengths. In the table we mark in bold the peaks which correspond to 
-the $E^{\parallel}_{100}$ mode.
 
@@
 
-Once we identify the proper modes, we proceed to the replication of Figure S4 on the 
-supplementary material of Ellis et al work. It is worth mentioning that we limit ourselves to
-the replication of the black curve in their plot, since in this case the pillars are separated 
-by 5000 nm which means the coupling effects are negligible. Figure \ref{fig:rep_FS4_ellis} shows
-the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
-with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
-the cases
-
 \begin{figure}
@@
 
-\subsubsection{Validation of \pygbe against Fig 2a experimental results}
+\subsubsection{Validation of \pygbe against Fig 2a experimental results, and replication of corresponfding computations}
 

### 2020-07-26 tex/results.tex
results.tex

@@
 
-For the case of aspect ratio four (AR=4) we obtain the smallest error using the uniform
-mesh. Since we count with the mesh provided by the authors, and knowing that our computation 
-for the mode $E^{\parallel}_{100}$ compares well with their computations, we attempted to 
-validate our simulations with their experimental results (red curve on paper), as well 
-as to replicate their simulations (green curve on paper) on Figure 2a of their paper.
+The results of Figure 2a on Ellis et al. were obtained on a pillar of aspect ratio $AR=4$. For this case,
+we count with the mesh provided by the authors. We also know that our computation 
+for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
+attempted to validate our simulations with their experimental results (red curve on paper), as well 
+as to replicate their simulations (green curve on paper).
 Figure 2a of Ellis et al, presents measured and simulated reflectance of SiC pillar
@@
 with no substrate, submerged in air under a constant electric field in the z-direction, 
-and rotate the orientation of the pillar to match the angle of incidence (see Figure \ref{fig:ellis_ang_inc}).
-In Figure \ref{fig:pygbe_vs_exp_2a} we present 
+and rotated the orientation of the pillar to match the angle of incidence used on Ellis et al. (see Figure \ref{fig:ellis_ang_inc}).
+In Figure \ref{fig:pygbe_vs_exp_2a} we present a 
 comparison of our simulations and the experimental results from Ellis et al. There is a 
@@
 material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
-mode by a shift of 12.17 cm$^-1$. Therefore as a \textit{first order correction} we can 
+mode by a shift of 12.17 cm$^-1$. Therefore, as a \textit{first order correction} we can 
 subtract this value from our simulations to count for coupling effects. In Figure 
@@
 particular P1 (837 cm$^-1$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
-do not discuss this result into detail, but they concentrate their analysis on the peaks
-that happen between 864–961 cm$^-1$
+do not discuss this result into detail, but they explain that these peaks go beyond the scope of the work, 
+they concentrate their analysis on the peaks that happen between 864–961 cm$^-1$
 

### 2020-07-26 tex/discussion.tex
add some points we should discuss

Discuss points (still need to check results, to see we haven't left some of this there):

Regarding Rockstuhl:

- The far right peak is probably because of 3D EFFECTS, the second peak, in the original runs, it was definitely related to the the 
sharp edges since when we introduce a level of roundness, it disappear. The peaks wavelength match perfectly, as seen in the Figure 
\ref{{fig:rep_14}}. We can say we replicate this result. 
Challenges: all what's on the replication list that should go in the background

Regarding Ellis:

Replication of Fig S4 supplementary material, was achieved successfully. 
Figure 2a validation and replication, achieved after correction for coupling. 
Challenges to validate with more results on the paper, since we did not count with enough 
information for the non-coupling case. So far we haven't attempted to run multiple pillars 
(ACTUALLY WE DID BUT I HAD THE WRONG NORMALS ON THE MESHES SO THE RESULTS WHERE TRASH), it is possible although we can not
introduce a substrate and have periodic boundary conditions.

In general:
- How hard is to replicate when you do not count with enough information regarding software, methods, mesh discretization, etc. 
- Challenges to access data, therefore relying on digitalization of plot that introduce a lot of human error, specially if the quality 
of the plot is bad like in Rockstuhl et al. 
- Validation can be complicated when there are no standards/benchmarks on the field.
- We can say our validation and replication studies, our reproducible. So hopefully this can be use as
 an example on the field.

### 2020-07-26 tex/background.tex
tweak text on physics context

@@
 
-In recent years, polar dielectrics such as Silicon Carbide (SiC) have caught the attention of researchers as an alternative to plasmonic metals, 
-due to their low optical losses in in the mid- to long-wave infrared range. 
+In recent years, polar dielectric crystals such as Silicon Carbide (SiC) became recognized as an alternative to plasmonic metals in many technologies, including biosensors. 
+They manifest oscillations of lattice-bound charges, called surface phonon polaritons, in the mid- to long-wave infrared range with low optical losses.
 Nanostructures made of these materials offer sensing capabilities, described by their \emph{figure of merits}, that are unattainable with plasmonic metals. 
@@
 $S = \Delta \lambda / \Delta n$.
-The dielectric of these materials has a negative real part and a very small imaginary part, in the mid/long infrared region. 
+The dielectric function of polar dielectrics has a negative real part and a small imaginary part, in the mid to long infrared regime. 
 This dielectric behavior is similar to that observed in metals like silver in the blue part of the wavelength spectrum. 
@@
 
-When studying both surface phonon polaritons and surface plasmon resonances, we can analyze the spectrums by measuring different quantities. 
+When studying both surface phonon polaritons and surface plasmon resonances, one can analyze the spectrums by measuring different quantities. 
 We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 

### 2020-07-26 tex/background.tex
edit repro sub-section

@@
 
-\begin{enumerate}
+\begin{compactitem}
 
@@
 
-\end{enumerate}
+\end{compactitem}
 
@@
 This condition is infrequently satisfied.
-The NASEM report describes how a number of systematic efforts to reproduce computational results have failed in more than half of the attempts made, mainly due to insufficient detail on digital artifacts, such as data, code and computational workflow \cite{moraila-etal-2014,iqbal-etal-2016,chang-li2018,stodden-etal-2018}.
+The NASEM report describes how a number of systematic efforts to reproduce computational results have failed in more than half of the attempts made, mainly due to inadequately specified or unavailable data, code and computational workflow \cite{moraila-etal-2014,iqbal-etal-2016,chang-li2018,stodden-etal-2018}.
 Recommendation 4-1 of the NASEM report states that 
@@
 
-Beyond the particulars of high-performance or parallel computing, what makes reproducibility so difficult to achieve? 
-A number of factors can contribute to the lack of reproducibility in research. 
-In addition to lack of access to non-public data and code, the NASEM report lists the following contributors to lack of reproducibility:
+Beyond the particulars of high-performance or parallel computing, 
+a number of factors can contribute to the lack of reproducibility in research. 
+In addition to lack of access to non-public data and code, the NASEM report (of which Barba is a co-author) lists the following contributors to lack of reproducibility:
 
-\begin{enumerate}
+\begin{compactitem}
 
-\item[$\triangleright$] Inadequate record-keeping: the original researchers did not properly record the relevant digital artifacts such as protocols or steps followed to obtain the results, the details of the computational environment and software dependencies, and/or information on the archival of all necessary data.
-\item[$\triangleright$]  Non-transparent reporting: the original researchers did not transparently report and provide open access to or archive the relevant digital artifacts necessary for reproducibility.
+\item[$\triangleright$] Inadequate record-keeping: the researchers did not properly document all relevant digital artifacts and steps followed to obtain the results, the details of the computational environment, software dependencies, and/or identifiers and metadata for data products.
+\item[$\triangleright$]  Lack of transparency: the researchers did not transparently report, using standard public licenses, an archive with all relevant digital artifacts necessary to reproduce the results.
 \item[$\triangleright$]  Obsolescence of the digital artifacts: over time, the digital artifacts in the research compendium are compromised because of technological breakdown and evolution or lack of continued curation.
 \item[$\triangleright$]  Flawed attempts to reproduce others' research: the researchers who attempted to reproduce the work lacked expertise or failed to correctly follow the research protocols.
-\item[$\triangleright$]  Barriers in the culture of research: lack of resources and incentives to adopt computationally reproducible and transparent research across fields and researchers.
+\item[$\triangleright$]  Barriers in the culture of research: lack of resources and incentives to adopt reproducible and transparent research across fields and researchers.
 
-\end{enumerate}
+\end{compactitem}
 
@@
 Scientific workflows represent a complex flow of data products through various steps of collection, transformation, and analysis to produce an interpretable result. 
-Capturing provenance of the result is increasingly difficult to do using manual processes. 
-Thus, to support computational reproducibility, efforts have been under way for several years to develop workflow-management systems that capture and store data and workflow provenance automatically. 
-With such systems, results can be reliably linked to the computational process that derived them, and computational tasks can be automated, allowing them to be rerun and shared.
+Capturing provenance of the result is increasingly difficult to do using manual processes, and automation is key. 
 With regards to software management, version-control systems are used to automatically capture the history of all changes made to the source code of a computer program. 
 This creates a history of changes and allows the developers to better understand the code and to identify possible problems or errors.
-Recently, the concept of version control has been extended to data files. 
-These files are generally too large to be stored in standard version-control systems, and they are often in a binary format that cannot be versioned. 
-Rather, data version control excludes the large data files from the main versioned repository, automatically collects data provenance, records data processing steps into a (reproducible) pipeline, and connects with cloud services where large data files are stored.
 Recent technological advances in version control, virtualization, computational notebooks, and automatic provenance tracking have the potential to simplify reproducibility, and tools have been developed that leverage these technologies.
-Still many questions remain answered both to understand the gaps left by existing tools and to develop principled approaches that fill those gaps.
+Still, many questions remain unanswered both to understand the gaps left by existing tools and to develop principled approaches that fill those gaps.
 

### 2020-07-26 tex/results.tex
edits Resuts 3(a)

--- 2020-07-26 tex/results.tex
@@
 The work of Rockstuhl et al.\cite{rockstuhl2005} studies the phonon-polariton response of silicon carbide (SiC)
-nanoparticles using the boundary element method. They analyze different ``cylindrical particles''
-made of 6H-SiC, as a function of geometrical cross-section. 
-They use a two-dimensional (2D) boundary element method 
-previously developed by the group \cite{rockstuhl2003}, where they extend in the third dimension to infinity
-(hence the name ``cylinder'').
+nanoparticles using a two-dimensional (2D) boundary element method, 
+previously developed in their group \cite{rockstuhl2003}. 
+They analyzed ``cylindrical particles'' (where they extend in the third dimension to infinity) made of 6H-SiC, with varying cross-sections.
 %%% Rockstuhl work summary%%%%
-
-We decided to attempt to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}:
+We decided to attempt to replicate one of the results presented on Fig.14 of their paper:
 the scattering cross-section of a SiC rectangular cylinder for three different aspect ratios. 
-To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
-dimension of the geometry), we chose the particular case where a=672 nm and b=328 nm.
+To be well within our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
+dimension of the geometry), we chose the case with $a=672$ nm, $b=328$ nm.
 
@@
 decided to use the default settings on Trimesh. 
-(For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod})
+For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
 Figure \ref{fig:tri_reg_round_14} shows the 
@@
 excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
-and computing polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
-width ($W=400$ nm) and varied length ($L=400-4800$ nm). These pillars are patterned on a squared 
-grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments they 
-perform polarized reflectance measurements with the incident polarization 
+polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
+width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
+($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
+to reduce coupling. In  both their simulations and experiments they excite the localized SPhP
+resonances, they perform polarized reflectance measurements with the incident polarization 
 oriented parallel or perpendicular to the long axis of the pillars.  
@@
 
-We first aim to replicate the computational result presented in Figure S4 of their supplementary 
-material that correspond to the black curve on their plot. In this 
+We aim to replicate the computational result presented in Figure S4 of their supplementary 
+material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
 figure they show simulation results for the resonance spectral position of the lower frequency 
 mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
-We attempted to replicate this result since the gap between the pillars 
-is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
-a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
-for the results presented in Figure 2a, in which they present reflectance measurements across wave number
-for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
-length of the pillars. This same case, counts with experimental results that we will use to attempt the validation of our solver.
+We first attempted to replicate this result since they have results where the gap between pillars 
+is 5000 nm (10 times more than in the experiments and other simulations on the paper), and 
+this diminishes the effects of coupling. This result is suitable to compare with 
+what we can model using \pygbe.
 
@@
 \textit{methods}
+(I DID NOT MENTION ANYTHING RELATED TO WHAT THEY DO IN THE EXPERIMENTS, SHOULD WE INCLUDE THIS?)
 
-In Ellis et al. they run experiments using reflectance spectroscopy and they compute the solution of
-Maxwell equations via the RF package of the finite element method software COMSOL. In their simulations 
-they use periodic boundary conditions of one pillar over a portion of substrate, to represent the array of 
-pillars and their interactions. 
-We use the boundary element method in the quasistatic approximation, which is suitable in these case 
-since the pillar's size is small compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). 
-We measure extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots). 
-The intensity of the peaks is not comparable, but we are looking to match the wave number (variable of interest) at which these events happen.
+In Ellis et al. simulations they solve full Maxwell equations via the RF package of the finite
+element method software COMSOL. To represent the array of pillars and their interactions, they use
+periodic boundary conditions of one pillar over a portion of substrate, and use periodic boundary conditions on it.
+They present the reflectance as a function of the wave number. 
+As we mentioned before, we use the boundary element method in 
+the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
+compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). We measure 
+extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots)
+since you see maximum extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
+looking to match the wave number (variable of interest) at which these events happen.
 
 \textit{mesh}
-
-For the case of aspect ratio $AR=4$ we count with a non-uniform triangular surface mesh (N=4398) provided by the authors of 
-Ellis et al, which we use for validation and replication of FIgure 2a of their paper. However, for the replication
-of Figure S4 of the supplementary material we needed the remaining aspect ratio meshes. We generated uniform meshes using our
-python script, and we determined the density of these meshes by comparing the extinction cross section for the case of AR=4 of 
-our mesh and the one provided by Ellis et al. We noticed that using around double the elements (N=8564) than in the original mesh and 
-rounding the edges, the relative errors for the extinction cross section where, on average, smaller than 3$\%$ and the variation on the wavelength peak
-occurrence was smaller than 1 cm$^-1$. This analysis lead us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
-the aspect ratio's variation study.
+For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
+Ellis et al. Which is a non-structured (HOW IS IT CALLED WHEN IS FINER WHER THERE ARE CORNERS?) mesh of
+approximately four thousand elements. To produce the remaining 
+meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
+After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
+uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
+I'M NOT SURE IF WE WANT TO PUT THEM).
+To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
+replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.
 
@@
  \subsection{Reproducibility and data management} \label{sec:reprod}
+
+ Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
+ A key element is professional software management and engineering, and the central technology solution is version control. 
+ Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
+ Another key element of transparent and reproducible computational modeling is \emph{automation}.
+Automating every step means \emph{turning protocols into code.}
+For example, simulations are launched with parameters fed from a configuration file rather than an interactive prompt, and all figures and plots are produced by writing scripts, rather than pointing-and-clicking on a graphical interface.
+The goal is to create complete ``recipes'' in code, which can be run, versioned, and shared.
+
+Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
+This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
+We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
+As in our previous papers, it is possible to reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo.
+[LIST, EXPLAIN, CITE ARCHIVES] 
+\pygbe is openly developed and shared under the BSD3-clause license via its repository at \url{https://github.com/barbagroup/pygbe}.

### 2020-07-26 tex/background.tex

@@
 
+\noindent
 The process of \emph{verification} establishes that a computational model correctly describes the intended mathematical equations and their solutions.
@@
 
+\noindent
 Improving computational reproducibility hinges on capturing and sharing information about the computational environment and steps required to collect, process, and analyze data.
@@
 Still, many questions remain unanswered both to understand the gaps left by existing tools and to develop principled approaches that fill those gaps.
+
+Replication of scientific findings is key for building trust in them. 
+It is often difficult to attain, for many reasons, not least because deciding when two scientific findings are \emph{consistent} is tangled in researcher judgements and inevitable constraints. 
+The NASEM report lists the following factors affecting the replicability of findings:
+
+\begin{compactitem}
+
+\item[$\triangleright$] the complexity of the system under study;
+\item[$\triangleright$] understanding of the number and relations among variables within the system under study;
+\item[$\triangleright$] the ability to control the variables; 
+\item[$\triangleright$] levels of noise within the system (or signal to noise ratios);
+\item[$\triangleright$] the mismatch of scale of the phenomena and the scale at which it can be measured; 
+\item[$\triangleright$] stability across time and space of the underlying principles; 
+\item[$\triangleright$] fidelity of the available measures to the underlying system under study (e.g., direct  or indirect measurements); and
+\item[$\triangleright$] prior probability (pre-experimental plausibility) of the scientific hypothesis.
+
+\end{compactitem}
+
+\noindent
+Fields of study that have been at the center of the `replication crisis` commotion tend to be characterized by their complexity, intrinsic variability, or inability to control variables, e.g., psychology.
+But in many areas of modern technology we face similar challenges to control variables or disentangle many interacting effects. 
+In this paper, we tackle replication and validation of computational models in nanoscale physics, where certainly the systems are complex, variables difficult to control, and signals subject to noise.
 

### 2020-07-26 tex/results.tex
minor fix
many fixes, results subsection (b)

@@
 the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
-presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
-successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
+presented in Figure \ref{fig:rep_14}: the main resonance peaks presented in Rockstuhl et al.\ are 
+closely matched. While we still have the presence of a third peak in our results, we conjecture 
 that this is a consequence of the 3D effects in our geometry.
@@
  %%% Ellis work summary %%%%
-The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
-resonant modes in localized surface phonon-polariton nanostructures. They study the
+The work of Ellis and coworkers \cite{ellis2016} studies the aspect-ratio evolution of high-order
+modes in localized surface phonon-polariton nanostructures. They study the
 excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
 and computing polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
-width ($W=400$ nm) and varied length ($L=400-4800$ nm). These pillars are patterned on a squared 
-grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments they 
-perform polarized reflectance measurements with the incident polarization 
+width ($W=400$ nm) and varied length ($L=400$--$4800$ nm). These pillars are patterned on a square 
+grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments, they 
+measured polarized reflectance with the incident polarization 
 oriented parallel or perpendicular to the long axis of the pillars.  
@@
 
-We first aim to replicate the computational result presented in Figure S4 of their supplementary 
-material that correspond to the black curve on their plot. In this 
-figure they show simulation results for the resonance spectral position of the lower frequency 
+Our first aim was to replicate the computational result presented in Figure S4 of their supplementary 
+material, corresponding to the black curve on their plot. In this 
+figure, they show simulation results for the resonance spectral position of the lower-frequency 
 mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
@@
 is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
-a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
-for the results presented in Figure 2a, in which they present reflectance measurements across wave number
-for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
-length of the pillars. This same case, counts with experimental results that we will use to attempt the validation of our solver.
+a good candidate to replicate using \pygbe. [SAY WHY]
+Our second attempted replication is  
+for the results presented in Figure 2a, corresponding to reflectance measurements across wave number
+for pillars with aspect ratio $AR=4$, angle of incidence of 22 degrees, and incoming polarization parallel to the 
+length of the pillars. For this case, the authors also reported experimental results that we will use for validation of our solver.
 
-\textbf{Difference between methods, mesh and dielectric data}
+\subsubsection{Differences in method, mesh and dielectric data}
 
-\textit{methods}
+\paragraph{Method:}
+Ellis et al.\ ran experiments using reflectance spectroscopy and they computed the solution of
+Maxwell's equations via the RF package of the finite element solver in the commercial software COMSOL. 
+In their simulations, 
+they used one pillar over a portion of substrate, with periodic boundary conditions to represent an array of 
+pillars and their interactions. 
+We use the boundary element method in the quasistatic approximation, which is suitable in this case 
+since the pillar's size is small compared to the wavelength involved in the simulations (800--1000 cm$^{-1}$, which is 10000--12500 nm). 
+We measure extinction cross section, which will express as peaks instead of depressions (shown in the reflection plots of Ellis et al.). 
+The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.
 
-In Ellis et al. they run experiments using reflectance spectroscopy and they compute the solution of
-Maxwell equations via the RF package of the finite element method software COMSOL. In their simulations 
-they use periodic boundary conditions of one pillar over a portion of substrate, to represent the array of 
-pillars and their interactions. 
-We use the boundary element method in the quasistatic approximation, which is suitable in these case 
-since the pillar's size is small compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). 
-We measure extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots). 
-The intensity of the peaks is not comparable, but we are looking to match the wave number (variable of interest) at which these events happen.
+\paragraph{Mesh:}
+For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
+Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
+of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
+Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
+our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
+rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
+position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
+the aspect ratio variation study.
 
-\textit{mesh}
-
-For the case of aspect ratio $AR=4$ we count with a non-uniform triangular surface mesh (N=4398) provided by the authors of 
-Ellis et al, which we use for validation and replication of FIgure 2a of their paper. However, for the replication
-of Figure S4 of the supplementary material we needed the remaining aspect ratio meshes. We generated uniform meshes using our
-python script, and we determined the density of these meshes by comparing the extinction cross section for the case of AR=4 of 
-our mesh and the one provided by Ellis et al. We noticed that using around double the elements (N=8564) than in the original mesh and 
-rounding the edges, the relative errors for the extinction cross section where, on average, smaller than 3$\%$ and the variation on the wavelength peak
-occurrence was smaller than 1 cm$^-1$. This analysis lead us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
-the aspect ratio's variation study.
-
-\textit{dielectric data}
-The dielectric data for the simulations, was given by the authors of the paper via a private communication, 
+\paragraph{Dielectric data:}
+The dielectric data for the simulations was given to us by the authors of the paper via a private communication, 
 and corresponds to experimental values of the dielectric.
 
-\subsubsection{Replication of Figure S4 of supplementary material of Ellis et al. 2016}
+\subsubsection{Replication of Figure S4 in the supplementary materials of Ellis et al., 2016}
 
-To be able to replicate the result of Figure S4 of the supplementary material of Ellis et al, we
-need to identify the lower frequency mode for each of
-the aspect ratios in our computations. For each aspect ratio (AR) 
-value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
-800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper) that is not a 
-longitudinal mode. The longitudinal mode appear only when we have an incidence angle that is off-normal, since 
-they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} show the results of the extinction 
-cross section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm), for normal 
-and 22 degrees angle of incidence. The simulations where performed 
-for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
-when having normal incidence as shown on see Figure \ref{fig:ellis_ang_inc}. From these results we select 
-the lower mode that it is not a longitudinal one and extract its wavelength (see \ref{tab:ar_peaks}) to replicate 
-\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
-with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
-the cases.
-
-Note: Ellis et al., changes the angle of incidence of the illuminating vector while in \pygbe we achieve this by
-rotating the geometry instead.
+To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
+need to identify the lower-frequency mode for each of
+the aspect ratios in our computations. For each aspect ratio ($AR$) 
+value from 1 to 7, we computed the extinction cross section $C_{ext}$ across the wave numbers in the range
+800--1000 $cm^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
+longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
+they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
+cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400$--$2800$ nm), for normal 
+and 22-degrees angle of incidence. The simulations where performed 
+for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
+when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
+the lowest mode that it is not a longitudinal one and extracted its wavelength (see \ref{tab:ar_peaks}) to replicate 
+\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
+with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
+(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
+rotated the geometry instead.)
 
@@
 
-\subsubsection{Validation of \pygbe against Fig 2a experimental results, and replication of corresponfding computations}
+\subsubsection{Validation of \pygbe against experimental results in Fig.\ 2a  of Ellis et al., and replication of the corresponding computations}
 
-The results of Figure 2a on Ellis et al. were obtained on a pillar of aspect ratio $AR=4$. For this case,
-we count with the mesh provided by the authors. We also know that our computation 
+The results of Figure 2a in Ellis et al.\ were obtained on a pillar of aspect ratio $AR=4$. For this case,
+we have the original mesh, provided to us by the authors. We also know that our computation 
 for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
-attempted to validate our simulations with their experimental results (red curve on paper), as well 
-as to replicate their simulations (green curve on paper).
-Figure 2a of Ellis et al, presents measured and simulated reflectance of SiC pillar
+attempted to validate our simulations with their experimental results (red curve on their paper), as well 
+as to replicate their simulations (green curve on their paper).
+Figure 2a of Ellis et al., presents measured and simulated reflectances of SiC pillar
 arrays with a 500 nm gap. All their measurements and simulations were performed with 
@@
 
-Using \pygbe we compute the extinction cross section of an isolated SiC pillar (AR=4)
-with no substrate, submerged in air under a constant electric field in the z-direction, 
-and rotated the orientation of the pillar to match the angle of incidence used on Ellis et al. (see Figure \ref{fig:ellis_ang_inc}).
-In Figure \ref{fig:pygbe_vs_exp_2a} we present a 
-comparison of our simulations and the experimental results from Ellis et al. There is a 
-difference in the peaks wavelength that is noticeable. This could be attributed to the
+Using \pygbe, we computed the extinction-cross section of an isolated SiC pillar ($AR=4$)
+with no substrate, submerged in air under a constant electric field in the $z$-direction, 
+and rotated the orientation of the pillar to match the angle of incidence used by Ellis et al.\ (see Figure \ref{fig:ellis_ang_inc}).
+In Figure \ref{fig:pygbe_vs_exp_2a}, we present a 
+comparison of our simulations and the experimental results of Ellis et al. A 
+difference in the wavelengths of the peaks is noticeable. This may be attributed to the
 fact that in their experiments the separation between pillars is of 500 nm, which implies
-there are coupling effects that in our simulations are not contemplated.
+there are coupling effects that in our simulations are not considered.
 
@@
 
-\paragraph{First order correction}
+\paragraph{First-order correction.}
 
-Since our simulations do not count for coupling effects, we can not strictly imitate 
-the conditions to validate our solver. However, from Figure S4 on the supplementary 
-material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
-mode by a shift of 12.17 cm$^-1$. Therefore, as a \textit{first order correction} we can 
-subtract this value from our simulations to count for coupling effects. In Figure 
-\ref{fig:val_2a} we present the result after applying the correction for coupling effects.
-It is worth mentioning that the far left (837 cm$^-1$) and far right (964 cm$^-1$) peaks 
-on Ellis results, are peaks associated with zone-folded LO (longitudinal) phonons, in 
-particular P1 (837 cm$^-1$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
-do not discuss this result into detail, but they explain that these peaks go beyond the scope of the work, 
-they concentrate their analysis on the peaks that happen between 864–961 cm$^-1$
+Since our simulations do not take into account coupling effects, we cannot strictly match 
+the conditions to validate our solver. However, from Figure S4 in the supplementary 
+materials of Ellis et al., we know that coupling effects affect the $E^{\parallel}_{100}$ 
+mode by a shift of 12.17 cm$^{-1}$. Therefore, as a \textit{first-order correction} we can 
+subtract this value from our simulations to account for coupling effects. In Figure 
+\ref{fig:val_2a}, we present the result after applying this correction for coupling effects.
+It is worth mentioning that the far-left (837 cm$^{-1}$) and far-right (964 cm$^{-1}$) peaks 
+on the results of Ellis et al., are peaks associated with zone-folded LO (longitudinal) phonons, in 
+particular P1 (837 cm$^{-1}$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
+do not discuss this result in detail, but they explain that these peaks go beyond the scope of the work; 
+they concentrate their analysis on the peaks that happen between 864 and 961 cm$^{-1}$.
+If we use the same approximation and compare the results with the simulations of Ellis et al.\ on
+Figure 2 of their paper (green curve), we get Figure \ref{fig:rep_2a}.
 
@@
  \end{figure}
-
-If we use the same approximation and compare the results with Ellis simulations on
-Figure 2 of their paper (green curve) we get (see Figure \ref{fig:rep_2a})
 

### 2020-07-26 tex/results.tex
fix two minor issues in results (b)

@@
 We attempted to replicate this result since the gap between the pillars 
-is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
-a good candidate to replicate using \pygbe. [SAY WHY]
+is 5000 nm (10 times larger than in the other cases), diminishing the effects of coupling, which makes it 
+a better candidate to replicate using \pygbe. 
+In our calculations, the setup consists of a single pillar, with no substrate.
 Our second attempted replication is  
@@
 We use the boundary element method in the quasistatic approximation, which is suitable in this case 
-since the pillar's size is small compared to the wavelength involved in the simulations (800--1000 cm$^{-1}$, which is 10000--12500 nm). 
+since the pillar's size is small compared to the wavelengths involved in the simulations: 
+which are in the range 10000--12500 nm. 
 We measure extinction cross section, which will express as peaks instead of depressions (shown in the reflection plots of Ellis et al.). 

### 2020-07-26 tex/discussion.tex
add discussion input to main tex
get started with discussion

@@
-Discuss points (still need to check results, to see we haven't left some of this there):
+%!TEX root = ClementiBarba2020.tex
+
+We have presented several results that replicate previous published findings in the general area of nanostructure responses to electromagnetic waves. 
+Our field of interest is computational nanoplasmonics for applications in biosensors, and in a previous publication we developed the mathematical formulation and reported both solution verification activities, and an application demo with our software \pygbe, extended to treat complex dielectrics.
+The search for a physical context and published results that would allow us to undertake validation studies with \pygbe is what led us to this work. 
+Even if we finally do have validation and replication cases, neatly presented here, the path to obtain these results was nonlinear, iterative, and arduous.
+
+In the first case, we sought to replicate a result from Rockstuhl et al., 2005 \cite{rockstuhl2005} where they computed the scattering cross-section as a function of wavelength for a silicon carbide nanostructure.
+They present their results as a plot, and report the numeric value of the resonance wavelength in the text. 
+Lacking access to the secondary data behind the plots---computed from two-dimensional simulations with a boundary element solver---we were forced to manually digitize the values from the figure.
+Our results are presented in Figure \ref{fig:rep_14}, together with the curve we obtain from digitizing the source image.
 
@@
 sharp edges since when we introduce a level of roundness, it disappear. The peaks wavelength match perfectly, as seen in the Figure 
-\ref{{fig:rep_14}}. We can say we replicate this result. 
+\ref{fig:rep_14}. We can say we replicate this result. 
 Challenges: all what's on the replication list that should go in the background

### 2020-07-26 tex/results.tex
use dip for inverted peak
get started with discussion

@@
 (green curve in Figure \ref{fig:tri_reg_round_14}) compare 
-with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
+with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by hand using 
 the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
@@
     \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
-    \caption{Replication of Figure 14 from Rockstuhl 2005. Extinction cross section of a
+    \caption{Replication of Figure 14 from Rockstuhl et al.\ 2005. Extinction cross section of a
     rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
@@
 which are in the range 10000--12500 nm. 
-We measure extinction cross section, which will express as peaks instead of depressions (shown in the reflection plots of Ellis et al.). 
+We measure extinction cross section, which will express as peaks instead of dips (shown in the reflection plots of Ellis et al.). 
 The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.
@@
 rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
-position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
+position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per Angstrom-squared to create the meshes for 
 the aspect ratio variation study.

### 2020-07-26 tex/discussion.tex
add to discussion

@@
 We have presented several results that replicate previous published findings in the general area of nanostructure responses to electromagnetic waves. 
-Our field of interest is computational nanoplasmonics for applications in biosensors, and in a previous publication we developed the mathematical formulation and reported both solution verification activities, and an application demo with our software \pygbe, extended to treat complex dielectrics.
+Our field of interest is computational nanoplasmonics for applications in biosensors, and in a previous publication we developed the mathematical formulation and reported both solution verification activities, and an application demo with our software \pygbe, extended to treat complex dielectrics and imposed electric fields \cite{ClementiETal2019}.
 The search for a physical context and published results that would allow us to undertake validation studies with \pygbe is what led us to this work. 
@@
 
-In the first case, we sought to replicate a result from Rockstuhl et al., 2005 \cite{rockstuhl2005} where they computed the scattering cross-section as a function of wavelength for a silicon carbide nanostructure.
-They present their results as a plot, and report the numeric value of the resonance wavelength in the text. 
+In the first case, we sought to replicate a result from Rockstuhl et al., 2005 \cite{rockstuhl2005}, where they computed the scattering cross-section as a function of wavelength for a silicon carbide rectangular nanostructure.
+They present their results as a plot (Figure 14 in their paper), and report the numeric value of the resonance wavelength in the text. 
 Lacking access to the secondary data behind the plots---computed from two-dimensional simulations with a boundary element solver---we were forced to manually digitize the values from the figure.
 Our results are presented in Figure \ref{fig:rep_14}, together with the curve we obtain from digitizing the source image. 
+We were successful at replicating the strong peaks reported  by Rockstuhl et al.\ at wavelengths
+10.42 $\mu m$ and 10.7 $\mu m$,  when the electric field $E$ is parallel to short side of the rectangle, and 10.42 $\mu m$ and 10.82 $\mu m$
+when $E$ is parallel to the long side. Our results contain extra (small) peaks that are not present in the work of Rockstul et al.
+The first one, located between the main two peaks, we attribute to the the effect of
+sharp edges (see Figure \ref{fig:tri_reg_round_14}). The second extra peak is the far right one, and we believe this
+peak is a consequence of the 3D nature of our geometry; as observed in Figure \ref{fig:ext_y_14} this peak intensity
+decreases as the third dimension of the geometry extends.
 

### 2020-07-26 tex/discussion.tex
add to discussion

@@
 In the first case, we sought to replicate a result from Rockstuhl et al., 2005 \cite{rockstuhl2005}, where they computed the scattering cross-section as a function of wavelength for a silicon carbide rectangular nanostructure.
-They present their results as a plot (Figure 14 in their paper), and report the numeric value of the resonance wavelength in the text. 
+They present their results as a plot (Figure 14 in their paper), and report the numeric value of the resonance wavelengths in the text. 
 Lacking access to the secondary data behind the plots---computed from two-dimensional simulations with a boundary element solver---we were forced to manually digitize the values from the figure.
@@
 We were successful at replicating the strong peaks reported  by Rockstuhl et al.\ at wavelengths
-10.42 $\mu m$ and 10.7 $\mu m$,  when the electric field $E$ is parallel to short side of the rectangle, and 10.42 $\mu m$ and 10.82 $\mu m$
+10.42 $\mu$m and 10.7 $\mu$ m,  when the electric field $E$ is parallel to short side of the rectangle, and 10.42 $\mu$m and 10.82 $\mu$ m
 when $E$ is parallel to the long side. Our results contain extra (small) peaks that are not present in the work of Rockstul et al.
 The first one, located between the main two peaks, we attribute to the the effect of
-sharp edges (see Figure \ref{fig:tri_reg_round_14}). The second extra peak is the far right one, and we believe this
+sharp edges (see Figure \ref{fig:tri_reg_round_14}), as when we introduce a level of roundness, it diminishes. The second extra peak is the far right one, and we believe this
 peak is a consequence of the 3D nature of our geometry; as observed in Figure \ref{fig:ext_y_14} this peak intensity
-decreases as the third dimension of the geometry extends.
+decreases as the third dimension of the geometry lengthens.
+The quantity of interest in these findings is the wavelength of the resonance peaks, and our results do indeed match the findings.
 
-Regarding Rockstuhl:
-
-- The far right peak is probably because of 3D EFFECTS, the second peak, in the original runs, it was definitely related to the the 
-sharp edges since when we introduce a level of roundness, it disappear. The peaks wavelength match perfectly, as seen in the Figure 
-\ref{fig:rep_14}. We can say we replicate this result. 
 Challenges: all what's on the replication list that should go in the background

### 2020-07-26 tex/discussion.tex
start discussion of second case

@@
 
+The second replication cases come from a paper by Ellis and co-workers \cite{ellis2016} studying the effect of aspect ratio on the excitation of high-order modes in localized surface phonon-polariton nanostructures.
+Their results in Figure 2 include experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings.
+Again, we lack access to the data behind the plots, and we had to digitize the curves by hand. 
+The quantity plotted in the original figures is reflectance as a function of wavenumber, whereas we compute the extinction---on the figures, they show inverted peaks, where we show positive peaks.
+We can compare the results, nevertheless, because the quantity of interest is the wavenumber position of the peaks.
+
 Challenges: all what's on the replication list that should go in the background

### 2020-07-26 tex/discussion.tex
add more to discussion of results (b)

@@
 We were successful at replicating the strong peaks reported  by Rockstuhl et al.\ at wavelengths
-10.42 $\mu$m and 10.7 $\mu$ m,  when the electric field $E$ is parallel to short side of the rectangle, and 10.42 $\mu$m and 10.82 $\mu$ m
+10.42 $\mu$m and 10.7 $\mu$ m,  when the electric field $E$ is parallel to the short side of the rectangle, and 10.42 $\mu$m and 10.82 $\mu$ m
 when $E$ is parallel to the long side. Our results contain extra (small) peaks that are not present in the work of Rockstul et al.
@@
 We can compare the results, nevertheless, because the quantity of interest is the wavenumber position of the peaks.
+Figure \ref{fig:pygbe_vs_exp_2a} shows the results of our simulations using \pygbe on an isolated pillar,
+compared with the experimental results of Ellis et al.\ on an array of pillars.
+The results with \pygbe  do not account for the effect of coupling among the pillars, which explains the noticeable discrepancy on the wave numbers at which the peaks occur. 
+We proposed a correction, based on the results reported on Figure S4 of Ellis et al.\ for the $AR=4$ case, where the shift on the wave number due to coupling is 12.17 cm$^{-1}$ (this value was obtained from digitized data).
+We subtract this value to that obtained with our simulations and we show the comparison of our corrected results against those of Ellis et al.: the experimental data on Figure \ref{fig:val_2a}, and the
+computational data on Figure \ref{fig:rep_2a}. 
+With this correction, we observe a good match of the wavenumber for the lower (and stronger) mode, while for the remaining modes a difference remains.
 

### 2020-07-26 tex/discussion.tex
ad discussion on ellis res

@@
 
-The second replication cases come from a paper by Ellis and co-workers \cite{ellis2016} studying the effect of aspect ratio on the excitation of high-order modes in localized surface phonon-polariton nanostructures.
+The second replication case come from a paper by Ellis and co-workers \cite{ellis2016} studying the effect of aspect ratio on the excitation of high-order modes in localized surface phonon-polariton nanostructures (Figure S4 of their supplementary material).
+Figure \ref{fig:rep_FS4_ellis} shows the results for this replication, where the relative errors between our computations and theirs is always smaller than 2$\%$.
+Having the smallest error for the case of $AR=4$ we proceed to study the results on Figure 2 of their work, which corresponds to teh same aspect ratio.
 Their results in Figure 2 include experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings.
@@
 The results with \pygbe  do not account for the effect of coupling among the pillars, which explains the noticeable discrepancy on the wave numbers at which the peaks occur. 
-We proposed a correction, based on the results reported on Figure S4 of Ellis et al.\ for the $AR=4$ case, where the shift on the wave number due to coupling is 12.17 cm$^{-1}$ (this value was obtained from digitized data).
+We proposed a correction, based on the results reported on Figure S4 of Ellis et al.\ for the $AR=4$ case, where the shift on the wave number due to coupling is 12.17 cm$^{-1}$ (difference between black and red curve for AR=4 on figure S4 of supplementary material).
 We subtract this value to that obtained with our simulations and we show the comparison of our corrected results against those of Ellis et al.: the experimental data on Figure \ref{fig:val_2a}, and the
 computational data on Figure \ref{fig:rep_2a}. 
-With this correction, we observe a good match of the wavenumber for the lower (and stronger) mode, while for the remaining modes a difference remains.
+When comparing with their experiments, once applied the correction, we observe a good match of the wavenumber for the lower (and stronger) mode, as well as a good match for the 
+third and fourth peaks.
+The wave number of the second peak, related to a longitudinal excitation (mode $L_{000}$ on Ellis et al.), presents a discrepancy that we believe it is related to the fact that our
+pillar does not have a substrate underneath. The remaining (fifth) peak, also presents a discrepancy, but in this case we can not identify the reason.
+It is worth mentioning that we do not include in the analysis the far left and far right peaks seen in the experimental results, since Ellis et al. do not discuss their 
+presence in detail (NOT SURE HOW TO FULLY EXPLAIN THIS.)
 

### 2020-07-26 tex/discussion.tex
comment on the peak we do not see

@@
 Having the smallest error for the case of $AR=4$ we proceed to study the results on Figure 2 of their work, which corresponds to teh same aspect ratio.
-Their results in Figure 2 include experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings.
+Their results in Figure 2a include experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings.
 Again, we lack access to the data behind the plots, and we had to digitize the curves by hand. 
@@
 pillar does not have a substrate underneath. The remaining (fifth) peak, also presents a discrepancy, but in this case we can not identify the reason.
-It is worth mentioning that we do not include in the analysis the far left and far right peaks seen in the experimental results, since Ellis et al. do not discuss their 
-presence in detail (NOT SURE HOW TO FULLY EXPLAIN THIS.)
+We did not analyze the peaks out of the range of 864-961 cm$^{-1}$, since Ellis et al. \ describe these peaks to be associated with zone-folded LO (longitudinal) phonons of 4H-SiC,
+what goes beyond the study of interest.
+After considering all this implications, we can say that we have validated our solver \pygbe against the experimental results of Figure 2a, as well as replicated their computations.
 

### 2020-07-26 tex/results.tex
comment on the peak we do not see

@@
 It is worth mentioning that the far-left (837 cm$^{-1}$) and far-right (964 cm$^{-1}$) peaks 
-on the results of Ellis et al., are peaks associated with zone-folded LO (longitudinal) phonons, in 
-particular P1 (837 cm$^{-1}$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
-do not discuss this result in detail, but they explain that these peaks go beyond the scope of the work; 
-they concentrate their analysis on the peaks that happen between 864 and 961 cm$^{-1}$.
+on the results of Ellis et al., are peaks associated with zone-folded LO (longitudinal) phonons of 4H-SiC,
+what goes beyond theirs \cite{ellis2016} and our paper. They concentrate their analysis on the peaks that happen between 864 and 961 cm$^{-1}$.
 If we use the same approximation and compare the results with the simulations of Ellis et al.\ on

### 2020-07-27 tex/discussion.tex
rough draft on closing discussions

@@
 
-Challenges: all what's on the replication list that should go in the background
+CHALLENGES
 
-Regarding Ellis:
+Throughout all the attempts of replication and validation, we face multiple challenges that started with the complexity of the system of study.
+In both papers we have systems that we were not able to fully
+model using \pygbe.
+For the case of Rockstuhl et al.\ the numerical method was the same, but the it was a 2D model instead of 3D like the one of \pygbe, while the computational work presented in Ellis et al.\ used a volumetric
+method, instead of a surface one like in \pygbe.
+Both works computed (or measured) quantities that were not the extinction cross section, but since there is a relation between their variables (scattering cross section or reflection)
+and ours (extinction cross section), through the wavelength (or wavenumber) at which the peaks happen, we have the quantity of interest in common.
+However, to produce the end results to compare against these works, we went through an
+exhaustive process of modeling, since we did not count with any information regarding the solvers, discretization, mesh, etc.
+In the case of Ellis et al.
+\ we benefited from multiple communications with some of the authors,
+who made available the geometry and mesh of the pillar, as well as the dielectric data needed as input for the simulations.
+Even though we appreciate this gesture, replication studies should not rely on communications with the authors.
+In both cases the secondary data that they use to achieve the results were not publicly available and we relied on a digitized version of them that we obtained.
+This work is tedious and introduce a lot of uncertainties that would be avoided by releasing
+the secondary data too.
 
-Replication of Fig S4 supplementary material, was achieved successfully. 
-Figure 2a validation and replication, achieved after correction for coupling. 
-Challenges to validate with more results on the paper, since we did not count with enough 
-information for the non-coupling case. So far we haven't attempted to run multiple pillars 
-(ACTUALLY WE DID BUT I HAD THE WRONG NORMALS ON THE MESHES SO THE RESULTS WHERE TRASH), it is possible although we can not
-introduce a substrate and have periodic boundary conditions.
+Validation has been a hard thing to achieve for our solver since the field does not count with benchmarks that are meant to be used for validation. Multiple times
+we encounter experimental results that we aim to replicate, but due to the lack of report on the conditions of the experiment, its setup and the geometries involved, 
+we have not been able to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors made possible to 
+attempt the validation.
 
-In general:
-- How hard is to replicate when you do not count with enough information regarding software, methods, mesh discretization, etc. 
-- Challenges to access data, therefore relying on digitalization of plot that introduce a lot of human error, specially if the quality 
-of the plot is bad like in Rockstuhl et al. 
-- Validation can be complicated when there are no standards/benchmarks on the field.
-- We can say our validation and replication studies, our reproducible. So hopefully this can be use as
- an example on the field.
+(try to connect all this challenges with what we wrote in the background about replication, we touch on all those bullet points)
+
+After all the challenges faced to achieve validation and replication of results, we can say that the process was not linear, 
+and the complexity involved increases if the work to be replicated or use for validation was not obtained through reproducible practices, and made open at the time 
+of publication. We believe that reproducible practices are needed so the work presented can be not only reproduced, but also 
+replicated and even used for validation studies if applicable.

### 2020-07-27 tex/results.tex
add notes on version and hardware

@@
 %!TEX root = ClementiBarba2020.tex
+All the results of these paper were obtained using \pygbe (\url{https://github.com/pygbe/pygbe})
+with the version at this point in the history of commits (\url{https://github.com/pygbe/pygbe/tree/e1f3650b0c99cab99dcfe5372200d3a1534eddfe}), which contains 
+the Dockerfile to create the image that was used for the containers where the simulations wherr run.
+
+All results were obtained on a lab workstation, built from parts.
+Hardware specifications are as follows: 
+\begin{itemize}
+  \item CPU: Intel Core i7-5930K Haswell-E 6-Core 3.5GHz LGA 2011-v3
+  \item RAM: G.SKILL Ripjaws 4 series 32GB (4 x 8GB)
+  \item GPU: Nvidia Tesla K40c (with 12 GB memory)
+\end{itemize}
 

### 2020-07-27 tex/results.tex
add info on times of main results

--- 2020-07-26 tex/results.tex
@@
 %!TEX root = ClementiBarba2020.tex
+All the results of these paper were obtained using \pygbe (\url{https://github.com/pygbe/pygbe})
+with the version at this point in the history of commits (\url{https://github.com/pygbe/pygbe/tree/e1f3650b0c99cab99dcfe5372200d3a1534eddfe}), which contains 
+the Dockerfile to create the image that was used for the containers where the simulations where run.
+
+All results were obtained on a lab workstation, built from parts.
+Hardware specifications are as follows: 
+\begin{itemize}
+  \item CPU: Intel Core i7-5930K Haswell-E 6-Core 3.5GHz LGA 2011-v3
+  \item RAM: G.SKILL Ripjaws 4 series 32GB (4 x 8GB)
+  \item GPU: Nvidia Tesla K40c (with 12 GB memory)
+\end{itemize}
+
+\textbf{Solver parameters}: We used a GMRES tolerance of $1\times10^{-6}$ for all our simulations. Details on the treecode and integration parameters, 
+can be found with input files the archive repository.
+
+\textbf{Run times:} We reported detailed time files along with the data of our simulations, that can be found in the repro-packs. However, 
+here is a small report.
+
+For the result of the replication of Figure 4 of Rockstuhl et al.\ the total time for each curve was approximately 11.6 hours, which is the result of computing
+the extinction cross section for 175 wavelength cases, what gives us $\approx$4 minutes per run. In the case of the validation and replication of Figure 2a of Ellis et al. \  
+the total time for the curve was approximately 2.3 hours, which is the result of computing
+the extinction cross section for 208 wavelength cases, what gives us $\approx$40 seconds per run.
 

### 2020-07-27 tex/discussion.tex
add some discussion

@@
 model using \pygbe.
-For the case of Rockstuhl et al.\ the numerical method was the same, but the it was a 2D model instead of 3D like the one of \pygbe, while the computational work presented in Ellis et al.\ used a volumetric
-method, instead of a surface one like in \pygbe.
-Both works computed (or measured) quantities that were not the extinction cross section, but since there is a relation between their variables (scattering cross section or reflection)
-and ours (extinction cross section), through the wavelength (or wavenumber) at which the peaks happen, we have the quantity of interest in common.
+For the case of Rockstuhl et al.\ even though they used boundary element methods it was a 2D model instead of 3D like the one implemented in \pygbe.
+The computational work presented in Ellis et al.\ used a volumetric
+method, while \pygbe is a surface one.
+Both works computed (or measured) quantities that were not the extinction cross section (computed in \pygbe), but since there is a relationship between their variables (scattering cross section and reflection)
+and ours (extinction cross section), via the wavelength (wavenumber) at which resonance happens, this was not a problem.
 However, to produce the end results to compare against these works, we went through an
-exhaustive process of modeling, since we did not count with any information regarding the solvers, discretization, mesh, etc.
+exhaustive process of modeling, assumptions making and even corrections.
+We did not count with any information regarding the solvers, discretization, meshes, etc.
 In the case of Ellis et al.
-\ we benefited from multiple communications with some of the authors,
-who made available the geometry and mesh of the pillar, as well as the dielectric data needed as input for the simulations.
+\ we benefited from multiple communications with the authors,
+who made available the geometry and mesh of the pillar, as well as the dielectric data used as input for the simulations.
 Even though we appreciate this gesture, replication studies should not rely on communications with the authors.
-In both cases the secondary data that they use to achieve the results were not publicly available and we relied on a digitized version of them that we obtained.
+In both cases the secondary data that presented in their results were not publicly available and we relied on a digitized version of them that we obtained.
 This work is tedious and introduce a lot of uncertainties that would be avoided by releasing
@@
 we encounter experimental results that we aim to replicate, but due to the lack of report on the conditions of the experiment, its setup and the geometries involved, 
-we have not been able to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors made possible to 
-attempt the validation.
-
-(try to connect all this challenges with what we wrote in the background about replication, we touch on all those bullet points)
+we have not been able to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al. \ made 
+possible the validation.
 

### 2020-07-27 tex/background.tex
small fix: background

@@
 New functions were added to read from configuration files the data describing the electric field, to compute the dipole moment, and to compute the final quantity of interest: extinction cross-section.
-We reported a major new release of the software in 2017 \cite{ClementiETal2017}, and later  presented the mathematical formulation for electromagnetic scattering in the long-wavelength setting and its associated continuum and discretized integral equations, and results including verification activities and a sensitivity calculations on a biosensor model \cite{ClementiETal2019}.
+We reported a major new release of the software in 2017 \cite{ClementiETal2017}, and later  presented the mathematical formulation for electromagnetic scattering in the long-wavelength setting and its associated continuum and discretized integral equations, and results including verification activities and sensitivity calculations on a biosensor model \cite{ClementiETal2019}.
 For verification, we conducted grid-convergence studies in two settings.
@@
 These verification activities build our confidence on the computational model---moreover, our work was published following careful reproducibility practices, including the release of reproducibility packages for all results.
-Nevertheless, the gold standard of confidence in the predictive capability of the model comes from validation: hunting for an opportunity to conduct validation studies with PyGBe in these settings led us through the twisted path that we report in this paper.
+Nevertheless, the gold standard of confidence in the predictive capability of the computational model comes from validation: our quest for an opportunity to conduct validation studies with PyGBe in these settings led us through the twisted path that we report in this paper.
 

### 2020-07-27 tex/results.tex
edit intro text on Results section

--- 2020-07-26 tex/results.tex
@@
 %!TEX root = ClementiBarba2020.tex
+All the results reported in this paper were obtained using the \pygbe software \cite{ClementiETal2017},
+with the version at commit \href{https://github.com/pygbe/pygbe/tree/e1f3650b0c99cab99dcfe5372200d3a1534eddfe}{34eddfe} in the history.
+The software GitHub repository contains a Dockerfile to create the container image where we ran the simulations. 
+The manuscript GitHub repository is separate from the software repository, and can be found at \url{https://github.com/barbagroup/pygbe_validation_paper}.
+It contains the reproducibility packages for all results, as described in sub-section \ref{sec:reprod} and elsewhere in the paper.
+We used a lab workstation for all simulations, built from parts.
+Hardware specifications are as follows: 
+\begin{compactitem}
+  \item[$\triangleright$] CPU: Intel Core i7-5930K Haswell-E 6-Core 3.5GHz LGA 2011-v3
+  \item[$\triangleright$] RAM: G.SKILL Ripjaws 4 series 32GB (4 x 8GB)
+  \item[$\triangleright$] GPU: Nvidia Tesla K40c (with 12 GB memory)
+\end{compactitem}
 
-\subsection{Replication of results from Rockstuhl, et al., 2005}
+\paragraph{Solver parameters:} We used a GMRES exit tolerance of $1\times10^{-6}$ in the iterative solver for all our simulations. Details on the treecode and integration parameters (and others)
+can be found within input files included in the manuscript GitHub repository as part of the reproducibility packages (``repro-packs'').
+
+\paragraph{Run times:} We report detailed time logs together with the data of our simulations, as part of the repro-packs to accompany this paper. Here is a brief report.
+For the result of the replication of Figure 14 of Rockstuhl et al., sub-section \ref{sec:replication1}, the total wall-clock time for producing each curve was approximately 11.6 hours, which is the result of computing
+the extinction cross section for 175 wavelength cases, giving $\approx$4 minutes per run.
+In the case of the validation and replication of Figure 2a of Ellis et al., sub-section \ref{sec:replication2},
+the total wall-clock time for producing the curve was approximately 2.3 hours, which is the result of computing
+the extinction cross section for 208 wavelength cases, giving $\approx$40 seconds per run.
+
+\subsection{Replication of results from Rockstuhl, et al., 2005}\label{sec:replication1}
 
@@
 
- \subsection{Replication of results from Ellis et al., 2016, and validation}
+ \subsection{Replication of results from Ellis et al., 2016, and validation}\label{sec:replication2}
 

### 2020-07-27 tex/results.tex
edit all captions

@@
     electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
-    as a function of wavelength divided by $L$.}
+    as a function of wavelength divided by $L$, for two mesh sizes as shown in the legend.}
     \label{fig:cube535}
@@
     \includegraphics[width=0.45\textwidth]{rockstuhl_rectangles.pdf} 
-    \caption{Rockstuhl runs configurations}
+    \caption{Configurations for the simulations corresponding to Fig. 14 of Rockstuhl et al., 2005.}
     \label{fig:rectangle_sketch}
@@
     \subfloat{\includegraphics[width=0.48\textwidth]{ext_y_14b.pdf}} 
-    \caption{Effect of the elongation of the third direction ($y$) on the 
-        extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm 
+    \caption{Effect of the elongation of the third dimension ($y$) on the 
+        extinction cross-section of a rectangular prism of SiC of dimensions $a=672$ nm 
         and $b=328$ nm, submerged in air and under a constant electric field 
-        parallel to the z-axis. The left plot corresponds to a configuration such that the electric 
+        parallel to the $z$-axis. The left plot corresponds to a configuration such that the electric 
         field is parallel to $b$ (configuration (A) on Figure \ref{fig:rectangle_sketch}), while the 
         right plot corresponds to a configuration such that the electric field is 
-        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}}
+        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}.}
     \label{fig:ext_y_14}   
@@
     \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14b.pdf}}
-    \caption{ Effect of uniformity and roundness on the mesh on the 
-    extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm, 
+    \caption{Effect of uniformity of the mesh and roundness of the edges on the 
+    extinction cross-section of a rectangular prism of SiC of dimensions $a=672$ nm, 
     $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
-    parallel to the z-axis}
+    parallel to the $z$-axis.}
     \label{fig:tri_reg_round_14}
@@
     \subfloat{\includegraphics[width=0.48\textwidth]{replication_14b.pdf}} 
-    \caption{Replication of Figure 14 from Rockstuhl et al.\ 2005. Extinction cross section of a
+    \caption{Replication of the results in Figure 14 of Rockstuhl et al., 2005. Extinction cross-section of a
     rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
-    in air and under a constant electric field parallel to the z-axis.}
+    in air and under a constant electric field parallel to the $z$-axis.}
     \label{fig:rep_14}
@@
 value from 1 to 7, we computed the extinction cross section $C_{ext}$ across the wave numbers in the range
-800--1000 $cm^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
+800--1000 cm$^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
 longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
 they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
-cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400$--$2800$ nm), for normal 
+cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$ nm) and varied length ($L=400$--$2800$ nm), for normal 
 and 22-degrees angle of incidence. The simulations where performed 
@@
     \includegraphics[width=0.45\textwidth]{ellis_ang_inc.pdf} 
-    \caption{Diagram of angles of incidence in \pygbe setup to comply with Ellis et al. disposition.}
+    \caption{Diagram showing the angles of incidence in our simulation setups to comply with the configuration in the case from Ellis et al.}
     \label{fig:ellis_ang_inc}
@@
     \includegraphics[width=0.8\textwidth]{AR_22_vs_norm.pdf} 
-    \caption{Extinction cross section across wave number for SiC pillars of multiple aspect ratios,  
-             (H=950 nm, W=400nm, L=400-2800 nm (AR=1-7)), where we have normal incidence and a 
-             22 degrees incidence.
+    \caption{Extinction cross-section across wavenumbers for SiC pillars of varying aspect ratios,  
+             ($H=950$ nm, $W=400$ nm, $L=400$--$2800$ nm, $AR=1$--$7$), with both normal incidence and a 
+             22-degree incidence.
             }
@@
       \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
-      field is parallel to the length (L) of the pillar. We have normal incidence and 22 degrees.}
+      field is parallel to the length ($L$) of the pillar. We have normal incidence and 22-degree incidence.}
       \label{tab:ar_peaks}
@@
     \includegraphics[width=0.85\textwidth]{AR_rep_FS4_Ellis2016.pdf} 
-    \caption{Replication of figure S4 of supplementary material of Ellis 2016. Wave
-    number at which happens the $E^{\parallel}_{100}$ mode for different aspect ratios.}
+    \caption{Replication of figure S4 in the supplementary materials of Ellis et al., 2016. Wave
+    number at which the $E^{\parallel}_{100}$ mode happens for different aspect ratios.}
     \label{fig:rep_FS4_ellis}
@@
     \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
-    \caption{\pygbe vs experiments of figure 2a of Ellis 2016. Ellis data 
-    was digitized with web digitizer.}
+    \caption{\pygbe vs.\ the experiments presented in Figure 2a of Ellis et al., 2016 (we obtained the data 
+    digitizing by hand from their figure using WebPlotDigitizer).}
     \label{fig:pygbe_vs_exp_2a}
@@
 
-Since our simulations do not take into account coupling effects, we cannot strictly match 
+Since our simulations do not take into account coupling effects in an array of prisms, we cannot strictly match 
 the conditions to validate our solver. However, from Figure S4 in the supplementary 
@@
 mode by a shift of 12.17 cm$^{-1}$. Therefore, as a \textit{first-order correction} we can 
-subtract this value from our simulations to account for coupling effects. In Figure 
+subtract this amount from our simulations to account for coupling effects. In Figure 
 \ref{fig:val_2a}, we present the result after applying this correction for coupling effects.
@@
 on the results of Ellis et al., are peaks associated with zone-folded LO (longitudinal) phonons of 4H-SiC,
-what goes beyond theirs \cite{ellis2016} and our paper. They concentrate their analysis on the peaks that happen between 864 and 961 cm$^{-1}$.
+an effect they say is beyond the scope of their analysis \cite{ellis2016}. They concentrate their analysis on the peaks that occur between 864 and 961 cm$^{-1}$.
 If we use the same approximation and compare the results with the simulations of Ellis et al.\ on
-Figure 2 of their paper (green curve), we get Figure \ref{fig:rep_2a}.
+Figure 2 of their paper (green curve), we obtain Figure \ref{fig:rep_2a}.
 

### 2020-07-27 tex/results.tex
missed two captions

@@
     \includegraphics[width=0.85\textwidth]{validation_FOA_fig2a_Ellis.pdf} 
-    \caption{Validation against experiments in figure 2a of Ellis 2016, using first order approximation}
+    \caption{Validation against experiments in Figure 2a of Ellis, et al., 2016, using the first-order correction, as explained in the text.}
     \label{fig:val_2a}
@@
     \includegraphics[width=0.85\textwidth]{replication_FOA_fig2a_Ellis.pdf} 
-    \caption{Replication of simulations in figure 2a of Ellis 2016, using first
-     order approximation}
+    \caption{Replication of the simulations in Figure 2a of Ellis et al., 2016, using the first-order correction, as explained in the text.}
     \label{fig:rep_2a}

### 2020-07-27 tex/results.tex
add to repro sub-section (c)  in results

@@
  Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility. 
+ Moreover, all our research software is developed in the open, and shared under permissive public licenses, such as BSD-3 or MIT License. 
+ These open licenses permit all uses, as well as derivative works, only subject to attribution.
  Another key element of transparent and reproducible computational modeling is \emph{automation}.
@@
 This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
-We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
-As in our previous papers, it is possible to reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo.
-[LIST, EXPLAIN, CITE ARCHIVES] 
-\pygbe is openly developed and shared under the BSD3-clause license via its repository at \url{https://github.com/barbagroup/pygbe}.
+We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short, and we have been doing this for many years and improving the process iteratively. 
+The basic steps were already contained in the ``Reproducibility PI Manifesto'' of 2012 \cite{barba2012manifesto}, where Barba pledged to always share a manuscript's data, plotting scripts and figures under CC-BY (Creative Commons Attribution license).
+Notably, this makes the figures re-usable by readers, without requiring them to ask permissions from the publisher, even if there was a transfer of copyright of the paper (the figures are included in the paper under the conditions of the public license).
+We later extended the practice to include all other digital artifacts associated with the results, beyond secondary data and figures. 
+As in our previous papers, readers can reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo. 
+They include Jupyter notebooks with all the plotting code, and also the manually digitized data from the figures in the source articles for our replication cases.
+Barba and Thiruvathukal, 2017 \cite{BarbaThiruvathukal2017}, explain that it is \emph{not enough} to provide these materials in a GitHub repository (the owner of a repository is always able to delete it), and one should deposit the reproducibility packages in an archival service providing a global identifier and permanent link (like a digital object identifier, DOI).
+%[LIST, EXPLAIN, CITE ARCHIVES] 
+The repository for this paper is at \url{https://github.com/barbagroup/pygbe_validation_paper}, which also includes the manuscript source files in LaTeX.
+The software repository for \pygbe is at \url{https://github.com/barbagroup/pygbe}.

### 2020-07-27 tex/discussion.tex
edit final portions of discussion section

--- 2020-07-26 tex/discussion.tex
@@
 
-The second replication case come from a paper by Ellis and co-workers \cite{ellis2016} studying the effect of aspect ratio on the excitation of high-order modes in localized surface phonon-polariton nanostructures (Figure S4 of their supplementary material).
+The second replication case is from a paper by Ellis and co-workers \cite{ellis2016} studying the effect of aspect ratio on the excitation of high-order modes in localized surface phonon-polariton nanostructures (Figure S4 of their supplementary material and Figure 2 of their paper).
 Figure \ref{fig:rep_FS4_ellis} shows the results for this replication, where the relative errors between our computations and theirs is always smaller than 2$\%$.
-Having the smallest error for the case of $AR=4$ we proceed to study the results on Figure 2 of their work, which corresponds to teh same aspect ratio.
-Their results in Figure 2a include experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings.
+The smallest error is for the case with $AR=4$ and we proceeded to study the results on Figure 2 of their work, corresponding to this same aspect ratio.
+Their results in Figure 2a include both experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings.
 Again, we lack access to the data behind the plots, and we had to digitize the curves by hand. 
@@
 The results with \pygbe  do not account for the effect of coupling among the pillars, which explains the noticeable discrepancy on the wave numbers at which the peaks occur. 
-We proposed a correction, based on the results reported on Figure S4 of Ellis et al.\ for the $AR=4$ case, where the shift on the wave number due to coupling is 12.17 cm$^{-1}$ (difference between black and red curve for AR=4 on figure S4 of supplementary material).
-We subtract this value to that obtained with our simulations and we show the comparison of our corrected results against those of Ellis et al.: the experimental data on Figure \ref{fig:val_2a}, and the
+We proposed a correction, based on the results reported on Figure S4 of Ellis et al.\ for the $AR=4$ case, where the shift on the wave number due to coupling is 12.17 cm$^{-1}$ (difference between black and red curves for $AR=4$ on figure S4 of the supplementary materials).
+We subtracted this value to that obtained with our simulations and we show the comparison of our corrected results against those of Ellis et al.: the experimental data on Figure \ref{fig:val_2a}, and the
 computational data on Figure \ref{fig:rep_2a}. 
-When comparing with their experiments, once applied the correction, we observe a good match of the wavenumber for the lower (and stronger) mode, as well as a good match for the 
+When comparing with their experiments, after the correction was applied, we observe a good match of the wavenumber for the lower (and stronger) mode, as well as a good match for the 
 third and fourth peaks.
-The wave number of the second peak, related to a longitudinal excitation (mode $L_{000}$ on Ellis et al.), presents a discrepancy that we believe it is related to the fact that our
+The wave number of the second peak, related to a longitudinal excitation (mode $L_{000}$ in Ellis et al.), presents a discrepancy that we believe is related to the fact that our
 pillar does not have a substrate underneath. The remaining (fifth) peak, also presents a discrepancy, but in this case we can not identify the reason.
-We did not analyze the peaks out of the range of 864-961 cm$^{-1}$, since Ellis et al. \ describe these peaks to be associated with zone-folded LO (longitudinal) phonons of 4H-SiC,
-what goes beyond the study of interest.
-After considering all this implications, we can say that we have validated our solver \pygbe against the experimental results of Figure 2a, as well as replicated their computations.
+We did not analyze the peaks out of the range 864--961 cm$^{-1}$, since Ellis et al. \ describe these peaks to be associated with zone-folded LO (longitudinal) phonons of 4H-SiC,
+and outside the scope of their study.
+After considering all these details, we can say that we have validated our solver \pygbe against the experimental results of Figure 2a, as well as replicated their computational results.
 
-Challenges: all what's on the replication list that should go in the background
+%CHALLENGES
 
-Regarding Ellis:
+Throughout all these activities aiming to replicate previous results and validate our computational model, we faced multiple challenges, starting with the complexity of the system under study.
+In both our source papers, we have systems that we were unable to fully
+model using \pygbe.
+For the case of Rockstuhl et al., even though they used a boundary element method, it was a 2D model instead of 3D like the one implemented in \pygbe.
+The computational work presented in Ellis et al.\ used a volumetric
+formulation (finite element method), whereas \pygbe implements a boundary integral one.
+Both works computed (or measured) quantities different from the extinction cross-section (computed in \pygbe), but given he relationship between their quantities (scattering cross-section and reflection)
+and ours (extinction cross section), via the wavelength (wavenumber) at which resonance happens, this was not a problem.
+To produce the end results for comparing against these works, however, we went through an
+exhaustive process of modeling, making assumptions, and even corrections.
+We were lacking any information regarding the solvers, discretization, meshes, etc., in the original papers.
+In the case of Ellis et al., we benefited from multiple communications with the authors,
+who made available the geometry and mesh of the pillar, as well as the dielectric data used as input for the simulations.
+Even though we appreciate this helpful interaction, replication studies should ideally not depend on communications with the original authors.
+In both cases, the secondary data presented in their results were not publicly available and we relied on a manually digitized version, obtained from the plots.
+This work is tedious and introduces uncertainties that would be avoided by releasing
+the secondary data.
 
-Replication of Fig S4 supplementary material, was achieved successfully. 
-Figure 2a validation and replication, achieved after correction for coupling. 
-Challenges to validate with more results on the paper, since we did not count with enough 
-information for the non-coupling case. So far we haven't attempted to run multiple pillars 
-(ACTUALLY WE DID BUT I HAD THE WRONG NORMALS ON THE MESHES SO THE RESULTS WHERE TRASH), it is possible although we can not
-introduce a substrate and have periodic boundary conditions.
+Validation has been a hard goal to achieve for our solver since the field does not have benchmarks that are meant to be used for validation. Multiple times,
+we encountered experimental results that we aspired to replicate, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
+we have unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 
+the validation possible.
 
-In general:
-- How hard is to replicate when you do not count with enough information regarding software, methods, mesh discretization, etc. 
-- Challenges to access data, therefore relying on digitalization of plot that introduce a lot of human error, specially if the quality 
-of the plot is bad like in Rockstuhl et al. 
-- Validation can be complicated when there are no standards/benchmarks on the field.
-- We can say our validation and replication studies, our reproducible. So hopefully this can be use as
- an example on the field.
+After all the challenges faced to achieve code validation and replication of results, we can say that the process was far from  linear, 
+and the complexity involved increases if the work to be replicated or used for validation was not conducted and published using reproducible practices, and made open at the time 
+of publication. We conclude that reproducible practices are needed not only for the work to be reproduced, but also 
+replicated and even used for validation studies, if applicable.

### 2020-07-27 tex/discussion.tex
add to abstract

@@
 we encountered experimental results that we aspired to replicate, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
-we have unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 
+we have been unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 
 the validation possible.

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_cube_15K.py
add repro_exec files rockstuhl

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'cube_535nm'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'cube_15K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/cube_535nm_res/'+'cube_15K'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_cube_19K.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'cube_535nm'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'cube_19K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/cube_535nm_res/'+'cube_19K'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_34K_LE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism3280x26880x6720_LE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_34K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_SE_LE_res/'+'prism_34K_long_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_34K_SE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism6720x26880x3280_SE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_34K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_SE_LE_res/'+'prism_34K_short_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_36K_LE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_328x1344x672nm_LE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_36K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_672x1344x328nm_res/'+'prism_36K_long_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_36K_SE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_672x1344x328nm_SE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_36K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_672x1344x328nm_res/'+'prism_36K_short_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_reg_36K_LE_y13K.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_reg_LE_y13K'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_reg_36K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_regular_SE_LE_res/'+'prism_reg_36K_LE_y13K'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_reg_36K_SE_y13K.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_reg_SE_y13K'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_reg_36K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_regular_SE_LE_res/'+'prism_reg_36K_SE_y13K'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_reg_38K_LE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_reg_LE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_reg_38K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_regular_SE_LE_res/'+'prism_reg_38K_long_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_reg_38K_SE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_reg_SE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_reg_38K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_regular_SE_LE_res/'+'prism_reg_38K_short_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_round_reg_38K_LE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_reg_round_LE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_reg_38K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_round_reg_SE_LE_res/'+'prism_round_reg_38K_long_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-27 repro_packs/rockstuhl/repro_exec_files/scripts/cext_wave_prism_round_reg_38K_SE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_permittivity_10-12_microns.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'prism_reg_round_SE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'prism_reg_38K.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/prism_round_reg_SE_LE_res/'+'prism_round_reg_38K_short_edge'+'10-20microns.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.9f %.9f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-27 tex/results.tex
add details of Zenodo archives

@@
 We later extended the practice to include all other digital artifacts associated with the results, beyond secondary data and figures. 
-As in our previous papers, readers can reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo. 
+As in our previous papers, readers can reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Zenodo. 
 They include Jupyter notebooks with all the plotting code, and also the manually digitized data from the figures in the source articles for our replication cases.
@@
 %[LIST, EXPLAIN, CITE ARCHIVES]
-The repository for this paper is at \url{https://github.com/barbagroup/pygbe_validation_paper}, which also includes the manuscript source files in LaTeX.
-The software repository for \pygbe is at \url{https://github.com/barbagroup/pygbe}.
+
+The following items of archived digital artifacts accompany this paper:
+
+\begin{compactitem}
+
+\item[$\triangleright$] The software repository for \pygbe is at \href{https://github.com/barbagroup/pygbe}{https://github.com/barbagroup/pygbe}.
+
+\item[$\triangleright$] The repository for this paper is at \href{https://github.com/barbagroup/pygbe_validation_paper}{https://github.com/barbagroup/pygbe\_validation\_paper}, which also includes the manuscript source files in LaTeX.
+
+\item[$\triangleright$] The problem datasets for replication of Rockstuhl et al., 2005, are in the manuscript repository, but also archived in Zenodo  at \href{https://doi.org/10.5281/zenodo.3962534}{10.5281/zenodo.3962534}  \cite{ClementiBarba2020-Zen_a}.
+
+\item[$\triangleright$] Execution files for all runs are archived in Zenodo at \href{https://doi.org/10.5281/zenodo.3962576}{10.5281/zenodo.3962576} \cite{ClementiBarba2020-Zen_b}.
+
+\item[$\triangleright$] The problem datasets for validation and replication of results from Ellis et al., 2016 are archived in Zenodo at \href{https://doi.org/10.5281/zenodo.3962584}{10.5281/zenodo.3962584}\cite{ClementiBarba2020-Zen_c}.
+
+\item[$\triangleright$] The file sets for reproducing the figures for the replication of results from Rockstuhl et al., 2005 are archived in Zenodo at \href{https://doi.org/10.5281/zenodo.
+3962791}{10.5281/zenodo.
+3962791} \cite{ClementiBarba2020-Zen_d}.
+
+\item[$\triangleright$] The file sets for reproducing the figures for the validation and replication of results from Ellis et al., 2017 are arhived in Zenodo at \href{https://doi.org/3962797/zenodo.3962791}{10.5281/zenodo.3962797} \cite{ClementiBarba2020-Zen_e}.
+
+\end{compactitem}

### 2020-07-29 repro_packs/ellis/repro_exec_files/extra/scripts/cext_wave_iso_pillar_long_edge.py
add ellis repro exec files

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'iso_pillar_long_edge'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar/'+'iso_pillar_long_edge'+'20-32Hz_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
+    time_simulation = (toc_ss - tic_ss) 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/extra/scripts/cext_wave_iso_pillar_long_edge_reg.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'iso_pillar_long_edge_reg_mesh'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_reg/'+'iso_pillar_long_edge'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/extra/scripts/cext_wave_iso_pillar_long_edge_round_4K.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'iso_pillar_LE_round_4K'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_round/'+'iso_pillar_long_edge_4K'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/extra/scripts/cext_wave_iso_pillar_long_edge_round_8K.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'iso_pillar_LE_round_8K'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_round/'+'iso_pillar_long_edge'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR1.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_1'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR/'+'iso_pillar_AR_1'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR1_22.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_1'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR_22deg/'+'iso_pillar_AR_1_22deg'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR2.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_2'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR/'+'iso_pillar_AR_2'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR2_22.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_2'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR_22deg/'+'iso_pillar_AR_2_22deg'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR3.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_3'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR/'+'iso_pillar_AR_3'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR3_22.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_3'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR_22deg/'+'iso_pillar_AR_3_22deg'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR4.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_4'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR/'+'iso_pillar_AR_4'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR4_22.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_4'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR_22deg/'+'iso_pillar_AR_4_22deg'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR4_22orig_LE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR4_LE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR4_22/'+'iso_pillar_AR4_22_LE'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR4_22orig_SE.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR4_SE'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR4_22/'+'iso_pillar_AR4_22_SE'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR5.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_5'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR/'+'iso_pillar_AR_5'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR5_22.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_5'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR_22deg/'+'iso_pillar_AR_5_22deg'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR6.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_6'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR/'+'iso_pillar_AR_6'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR6_22.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_6'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR_22deg/'+'iso_pillar_AR_6_22deg'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR7.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_7'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR/'+'iso_pillar_AR_7'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-07-29 repro_packs/ellis/repro_exec_files/scripts/cext_wave_iso_pillar_AR7_22.py

@@ -1,0 +1,71 @@
+import numpy
+import time
+import sys
+import os
+from argparse import ArgumentParser
+
+import pygbe
+from pygbe.util.read_data import read_fields
+from pygbe.main import main
+
+from cext_wavelength_scanning import create_diel_list, Cext_wave_scan, Cext_analytical
+
+
+def read_inputs(args):
+    """
+    Parse command-line arguments to read arguments in main.
+    """
+
+    parser = ArgumentParser(description='Read path where input files are located')
+    parser.add_argument('-if',
+                        '--infiles',
+                        type=str,
+                        help="Absolute path where input files are located (downloaded from zenodo)")
+    
+    return parser.parse_args(args)
+    
+
+
+def main(argv=sys.argv):
+
+    argv=sys.argv
+    args = read_inputs(argv[1:])
+
+    in_files_path = args.infiles
+
+    #Import surface data
+    wave_s, diel_rs, diel_is = numpy.loadtxt('../dielectric_data/4H-SIC_Angs_permittivity_800-1000cm-1.csv', skiprows=1, unpack=True)
+
+    air_diel = [1. + 1j*0.] * len(wave_s)
+    #Creating dielectric list first dielectric outside, then inside
+    diel_list = [list(eps) for eps in zip(air_diel, diel_rs + 1j*diel_is)]
+
+    #Set enviornment variable for PyGBe
+    folder_path = in_files_path + 'AR_7'
+    full_path = os.path.abspath(folder_path)+'/'
+    os.environ['PYGBE_PROBLEM_FOLDER'] = full_path
+
+    #Creating dictionary field. We will modify the 'E' key in the for loop.
+    field_dict_pillars = read_fields(full_path + 'iso_pillar.config')
+
+
+    #Calculate Cext(lambda) for pillars' surface
+    tic_ss = time.time()
+    e_field = -1.
+    wave, Cext_pillars = Cext_wave_scan(e_field, wave_s, diel_list, field_dict_pillars, full_path) 
+    toc_ss = time.time()
+
+
+
+    numpy.savetxt('../results_data/iso_pillar_AR_22deg/'+'iso_pillar_AR_7_22deg'+'_800-1000cm-1_in_ang.txt', 
+                  list(zip(wave, Cext_pillars)),
+                  fmt = '%.5f %.5f', 
+                  header = 'lambda [Ang], Cext [nm^2]') 
+
[…]

### 2020-09-01 tex/discussion.tex
Fix typo trecode -> treecode
Fix typo mode -> modes

Fix typo, repetion aa -> a

Fix typo given he -> given the

@@
 formulation (finite element method), whereas \pygbe implements a boundary integral one.
-Both works computed (or measured) quantities different from the extinction cross-section (computed in \pygbe), but given he relationship between their quantities (scattering cross-section and reflection)
+Both works computed (or measured) quantities different from the extinction cross-section (computed in \pygbe), but given the relationship between their quantities (scattering cross-section and reflection)
 and ours (extinction cross section), via the wavelength (wavenumber) at which resonance happens, this was not a problem.

### 2020-09-01 tex/results.tex
Fix typo trecode -> treecode
Fix typo mode -> modes

Fix typo, repetion aa -> a

Fix typo given he -> given the

@@
 
-\paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a a source that we
+\paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a source that we
 were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 

### 2020-09-01 tex/background.tex
fix different PyGBe writings, replace all for /pygbe

@@
 
-\subsection{Description of the PyGBe software}
+\subsection{Description of the \pygbe software}
 
-Our research group has been developing PyGBe---pronounced \emph{pigb\={e}}---for several years. 
+Our research group has been developing \pygbe---pronounced \emph{pigb\={e}}---for several years. 
 It was first written for biomolecular-electrostatics calculations using a continuum model of proteins in water or an ionic solvent. 
@@
 Biomolecules are modeled as dielectric cavities inside an infinite continuum solvent, and the partial differential equations are solved via a boundary element method, leading to a dense linear system of equations.
-PyGBe uses a fast-summation algorithm via a Barnes-Hut treecode \cite{BarnesHut1986}, and accelerates the computationally intensive parts of the code on Nvidia GPU hardware using CUDA kernels in the treecode, interfacing with PyCUDA \cite{klockner2012pycuda}.
+\pygbe uses a fast-summation algorithm via a Barnes-Hut treecode \cite{BarnesHut1986}, and accelerates the computationally intensive parts of the code on Nvidia GPU hardware using CUDA kernels in the treecode, interfacing with PyCUDA \cite{klockner2012pycuda}.
 Other portions of the code are written in C$++$, wrapped using \texttt{swig}, to extract more performance \cite{CooperETal2016}. 
-These features allow PyGBe to handle problems with half a million boundary elements or more.
+These features allow \pygbe to handle problems with half a million boundary elements or more.
 
-In more recent work, we expanded the capabilities of PyGBE to applications of computational nanoplasmonics for biosensing \cite{ClementiETal2019}. 
+In more recent work, we expanded the capabilities of \pygbe to applications of computational nanoplasmonics for biosensing \cite{ClementiETal2019}. 
 Applying the long-wavelength limit, one can model the phenomenon of localized surface plasmon resonance (LSPR) via electrostatics, instead of the full Maxwell equations. 
@@
 Since the resonance frequency depends on the dielectric environment, the change produced by a biomolecule approaching the metallic nanoparticle results in a frequency shift, and a means of detecting its presence.
-The electrostatic approximation allows using the methods implemented in PyGBe, after substantial code development to permit using complex-valued permittivities, and to incorporate an external electric field into the model.
+The electrostatic approximation allows using the methods implemented in \pygbe, after substantial code development to permit using complex-valued permittivities, and to incorporate an external electric field into the model.
 These changes included re-writing the Krylov iterative solver to work with complex numbers, and splitting the treecode evaluation into real and imaginary parts. 
@@
 These verification activities build our confidence on the computational model---moreover, our work was published following careful reproducibility practices, including the release of reproducibility packages for all results.
-Nevertheless, the gold standard of confidence in the predictive capability of the computational model comes from validation: our quest for an opportunity to conduct validation studies with PyGBe in these settings led us through the twisted path that we report in this paper.
+Nevertheless, the gold standard of confidence in the predictive capability of the computational model comes from validation: our quest for an opportunity to conduct validation studies with \pygbe in these settings led us through the twisted path that we report in this paper.
 

### 2020-09-02 tex/results.tex
Add explanation of labels on Fig as suggested for rev 1

@@
     $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
-    parallel to the $z$-axis.}
+    parallel to the $z$-axis. Where the labels are \textbf{Trimesh}: for non-uniform mesh generated using Trimesh; 
+    \textbf{Uniform}: for uniform mesh generated using python scripts; and 
+    \textbf{Uni + round}: for uniform mesh generated using python scripts with round 
+    edges obtained using Trimesh.}
     \label{fig:tri_reg_round_14}

### 2020-09-02 tex/results.tex
Add a better explanation of Fig4 results (suggested rev 1)

@@
 Figure \ref{fig:tri_reg_round_14} shows the 
-results of the effect of uniformity and roundness. One can see that the second peak is not
-present in the green curve, which can be attributed to the effect of the roundness. This is 
-consistent with the results in Rockstuhl et al.
+results of the effect of uniformity and roundness. One can see that the second peak in the $E\parallel b$ plot located at $\approx$ 10.6 $\mu$m  is not
+present in the green curve, and the intensity for the second peak in the $E\parallel a$ plot located at $\approx$ 10.6 $\mu$m diminishes. These effects can be attributed 
+to the effect of the roundness. This is consistent with the results in Rockstuhl et al.
 

### 2020-09-03 tex/results.tex
small typos

@@
     $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
-    parallel to the $z$-axis. Where the labels are \textbf{Trimesh}: for non-uniform mesh generated using Trimesh; 
-    \textbf{Uniform}: for uniform mesh generated using python scripts; and 
-    \textbf{Uni + round}: for uniform mesh generated using python scripts with round 
+    parallel to the $z$-axis. The labels are: \textbf{Trimesh}, for a non-uniform mesh generated using Trimesh; 
+    \textbf{Uniform}, for a uniform mesh generated using Python scripts; and 
+    \textbf{Uni + round}, for a uniform mesh generated using Python scripts with round 
     edges obtained using Trimesh.}

### 2020-09-03 tex/results.tex
shorten sentence

@@
 Figure \ref{fig:tri_reg_round_14} shows the 
-results of the effect of uniformity and roundness. One can see that the second peak in the $E\parallel b$ plot located at $\approx$ 10.6 $\mu$m  is not
-present in the green curve, and the intensity for the second peak in the $E\parallel a$ plot located at $\approx$ 10.6 $\mu$m diminishes. These effects can be attributed 
+results of the effect of uniformity and roundness.
+One can see that the second peak located at $\approx$ 10.6 $\mu$m  is much diminished in the green curve for both the $E\parallel b$  the $E\parallel a$ plots.
+These effects can be attributed 
 to the effect of the roundness. This is consistent with the results in Rockstuhl et al.

### 2020-09-04 tex/results.tex
Add labels explanation on Fig 1

@@
     electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
-    as a function of wavelength divided by $L$, for two mesh sizes as shown in the legend.}
+    as a function of wavelength divided by $L$, for mesh sizes 19K = 19,200 triangles and 15K = 15,552 triangles. 
+    The label "diff" refers to the difference between the results of the two meshes.}
     \label{fig:cube535}

### 2020-09-04 tex/results.tex

@@
 rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
-position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per Angstrom-squared to create the meshes for 
+position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per $\text{\AA}$ squared to create the meshes for 
 the aspect ratio variation study.

### 2020-09-05 tex/results.tex
Add sentence to explain y values limitation
small rewrite
fix passage mentioned by Rockstul in email

@@
 We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
-But, since the quantity of interest is the wavelength at which the resonance modes occur, the results can be compared.
+Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
+Nevertheless, the quantity of interest is the wavelength at which the peaks occur, and the main peaks for scattering and absorption do occur at nearly the same frequency, in this regime. 
+For example, Wiley et al.\ show simulatinon results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.
 
@@
 intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
-from now on we use $y=2688$ nm.
+from now on we use $y=2688$ nm. We did not explore larger values of $y$ because of the limitations imposed by the quasistatic limit model.
 

### 2020-09-05 tex/results.tex
fix word choice
mention in caption ata from Rockstuhl is scattering

@@
 compared to the results of Figure 18 of Rockstuhl et al., due to the three-dimensional effects captured in our simulation and the sharp 
-edges, the latter effect also being mentioned by Rockstuhl et al. The 3D effects will be approached
+edges, the latter effect also being mentioned by Rockstuhl et al. The 3D effects will be addressed
 in the following results, where we attempt a replication of one of the results on Figure 14 of Rockstuhl et al.
@@
 closely matched. While we still have the presence of a third peak in our results, we conjecture 
-that this is a consequence of the 3D effects in our geometry.
+that this is a consequence of the 3D effects in our geometry, 
+as well as the fact that we compute extinction cross-section, while Rockstuhl et al.\ report scattering.
 
@@
     rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
-    in air and under a constant electric field parallel to the $z$-axis.}
+    in air and under a constant electric field parallel to the $z$-axis (green line). 
+    The digitized curve from Rockstuhl et al.\ corresponds to scattering (orange line).}
     \label{fig:rep_14}

### 2020-09-07 tex/results.tex
remove absorption vs scattering as a cause

@@
 closely matched. While we still have the presence of a third peak in our results, we conjecture 
-that this is a consequence of the 3D effects in our geometry, 
-as well as the fact that we compute extinction cross-section, while Rockstuhl et al.\ report scattering.
+that this is a consequence of the 3D effects in our geometry.
 

### 2020-09-15 tex/results.tex
Fix typo
fix typo on dielectric name

@@
 Nevertheless, the quantity of interest is the wavelength at which the peaks occur, and the main peaks for scattering and absorption do occur at nearly the same frequency, in this regime. 
-For example, Wiley et al.\ show simulatinon results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.
+For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.
 
@@
 \paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a source that we
-were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
+were not able to replicate. Instead we are using experimental data for 4H-SiC that was provided to us 
 via private communications from the authors of Ellis et al.\cite{ellis2016}.

### 2020-09-21 tex/results.tex
Final tweak

@@
 Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
-Nevertheless, the quantity of interest is the wavelength at which the peaks occur, and the main peaks for scattering and absorption do occur at nearly the same frequency, in this regime. 
-For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.
+When the resonance peaks are sharp and narrow, the wavelengths at which they occur in the scattering and absorption spectra are nearly the same.
+For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are close \cite{wiley-etal-2006}.  
+Since silicon carbide has more pronounced peaks than silver, the wavelength at which they occur in the extinction and scattering spectra are more closely aligned.
 

### 2020-09-22 tex/background.tex
more precision in 2(c)

@@
 \item[$\triangleright$] Verification must precede validation.
-\item[$\triangleright$] The need for validation experiments and the associated accuracy requirements for computational model predictions are based on the intended use of the model.
+\item[$\triangleright$] Needs for validation experiments and associated accuracy requirements for computational model predictions are based on the intended use of the model.
 \item[$\triangleright$] Validation of a complex system should be pursued in a hierarchical fashion from the component level to the system level.
@@
 When studying both surface phonon polaritons and surface plasmon resonances, one can analyze the spectrums by measuring different quantities. 
-We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
-These different approaches are comparable since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen. 
-Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
+We can measure scattering cross-section, absorption, or extinction cross-section (scattering plus absorption), as well as reflection. 
+Since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen, 
+these different approaches are comparable in some cases, e.g., whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
 Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 

### 2020-09-22 tex/results.tex
minor edits, results section

@@
 We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
-Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
-When the resonance peaks are sharp and narrow, the wavelengths at which they occur in the scattering and absorption spectra are nearly the same.
+Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not generally comparable. 
+When the resonance peaks are sharp and narrow, however, the wavelengths at which they occur in the scattering and absorption spectra are nearly the same.
 For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are close \cite{wiley-etal-2006}.  
@@
 Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
- to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
+ to 19,200 triangles (density $1.11\times10^{-5}$ per $\text{\AA}$ squared):
  the computed results show no discernible difference.
@@
 These effects can be attributed 
-to the effect of the roundness. This is consistent with the results in Rockstuhl et al.
+to the roundness, consistent with the results in Rockstuhl et al.
 
@@
 figure, they show simulation results for the resonance spectral position of the lower-frequency 
-mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
+mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22 degrees.
 We attempted to replicate this result since the gap between the pillars 
@@
 for the results presented in Figure 2a, corresponding to reflectance measurements across wave number
-for pillars with aspect ratio $AR=4$, angle of incidence of 22 degrees, and incoming polarization parallel to the 
+for pillars with aspect ratio $AR=4$, angle of incidence 22 degrees, and incoming polarization parallel to the 
 length of the pillars. For this case, the authors also reported experimental results that we will use for validation of our solver.
@@
 since the pillar's size is small compared to the wavelengths involved in the simulations: 
-which are in the range 10000--12500 nm. 
-We measure extinction cross section, which will express as peaks instead of dips (shown in the reflection plots of Ellis et al.). 
+in the range 10000--12500 nm. 
+We measured extinction cross section, which will express as peaks instead of dips (shown in the reflection plots of Ellis et al.). 
 The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.
@@
 of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
-Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
-our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
-rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
-position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per $\text{\AA}$ squared to create the meshes for 
+Python script, and we determined the density of these meshes by comparing the extinction cross-section for the case with $AR=4$ of 
+our mesh and the one provided by Ellis et al. We noticed that using around double the number of elements ($N=8564$) than in the original mesh and 
+rounding the edges, the relative errors for the extinction cross-section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
+position was smaller than 1 cm$^{-1}$. This analysis led us to a density of $\approx \; 1.7 \times10^{-5}$ triangles per $\text{\AA}$ squared to create the meshes for 
 the aspect ratio variation study.
@@
 the aspect ratios in our computations. For each aspect ratio ($AR$) 
-value from 1 to 7, we computed the extinction cross section $C_{ext}$ across the wave numbers in the range
+value from 1 to 7, we computed the extinction cross-section $C_{ext}$ across the wave numbers in the range
 800--1000 cm$^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
@@
 when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
-the lowest mode that it is not a longitudinal one and extracted its wavelength (see \ref{tab:ar_peaks}) to replicate 
-\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
+the lowest mode that is not a longitudinal one and extracted its wavelength (see Table \ref{tab:ar_peaks}) to replicate 
+Figure \ref{fig:rep_FS4_ellis}. This figure shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
 with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
@@
 as to replicate their simulations (green curve on their paper).
-Figure 2a of Ellis et al., presents measured and simulated reflectances of SiC pillar
-arrays with a 500 nm gap. All their measurements and simulations were performed with 
+Figure 2a of Ellis et al.\ presents measured and simulated reflectances of SiC pillar
+arrays with a 500-nm gap. All their measurements and simulations were performed with 
 22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
@@
 difference in the wavelengths of the peaks is noticeable. This may be attributed to the
-fact that in their experiments the separation between pillars is of 500 nm, which implies
+fact that in their experiments the separation between pillars is 500 nm, which implies
 there are coupling effects that in our simulations are not considered.

### 2020-09-22 tex/discussion.tex
tweaks discussion section

--- 2020-07-27 tex/discussion.tex
@@
 sharp edges (see Figure \ref{fig:tri_reg_round_14}), as when we introduce a level of roundness, it diminishes. The second extra peak is the far right one, and we believe this
-peak is a consequence of the 3D nature of our geometry; as observed in Figure \ref{fig:ext_y_14} this peak intensity
+peak is a consequence of the 3D nature of our geometry; as observed in Figure \ref{fig:ext_y_14}, this peak intensity
 decreases as the third dimension of the geometry lengthens.
@@
 formulation (finite element method), whereas \pygbe implements a boundary integral one.
-Both works computed (or measured) quantities different from the extinction cross-section (computed in \pygbe), but given he relationship between their quantities (scattering cross-section and reflection)
-and ours (extinction cross section), via the wavelength (wavenumber) at which resonance happens, this was not a problem.
+Both works computed (or measured) quantities different from the extinction cross-section (computed in \pygbe), but given the relationship between their quantities (scattering cross-section and reflection)
+and ours (extinction cross-section), via the wavelength (wavenumber) at which resonance happens, this was not a problem.
 To produce the end results for comparing against these works, however, we went through an

### 2020-09-22 Response_to_reviewers.md
add response to reviewers

# Response to reviewers

## Reviewer 1 comments

This is a nicely written report that provides an important demonstration of high-quality V&V and R&R. The effort of the group to provide all materials and act as a positive example for the computational community is commendable. The report also benefits from a deep and informative background section; a positive aspect and a good fit for a journal such as Phil. Transactions A.

Minor comments:

- [x]  Pg 2 line 26 – trecode should be treecode
- [x]  Pg 2 line 36 – mode should be modes
- [x]  Pg 8 line 39 – there is repetition of ‘a a’
- [x]  Pg 9, and elsewhere, when discussing the features of the figures, in the case of Pg 9 it is figure 4, it would be useful to be more descriptive, for instance “One can see that the second peak in the E||b plot at 10.6 um is not present for the green curve”
- [x]  In the Figure 4 caption it would be useful to briefly explain the legend terms: trimesh, uniform and uni + round.
- [x]  Pg 12 line 27 – change “per Angstrom-squared” to use the Angstrom symbol and rewrite?
- [x] Pg 19 line 19 – given he relationship

**Changes**

Commit: [c5095c3](https://github.com/barbagroup/pygbe_validation_paper/commit/c5095c31761e7092858b21a43a16d39aadbd0912)

- In abstract:
trecode -> treecode
position of some mode -> position of some modes 
- In results:
a a -> a 
- In discussion:
given he -> given the

Commit: [b060520](https://github.com/barbagroup/pygbe_validation_paper/pull/4/commits/b0605200ac6928998e75a2a9667889e69c81639d),
commit [50d7357](https://github.com/barbagroup/pygbe_validation_paper/commit/50d73572fa65f8823dfed09342a490ee55ed284e)
- Explain legends in caption

Commit [bf14a0a](https://github.com/barbagroup/pygbe_validation_paper/commit/bf14a0ae0122e371ea6180c230b5196ee329aef8) - better explain Fig. 4

Commit: [6f5dec](https://github.com/barbagroup/pygbe_validation_paper/pull/4/commits/6f5decbc6a101b8c38c6e83b0b772b7e0f648b17)
- Use Angstrom symbol

## Reviwer 2 comments

It was a pleasure to review the manuscript “Reproducible Validation and Replication Studies in Nanoscale Physics” by Clementi and Barba. This paper presents validation and replication studies in area of nanostructure responses to electromagnetic waves. The authors use their previously developed open-source software PyGBe to replicate results from previous publications. The authors make their reproducibility packages openly accessible, including the computational software, input files, execution scripts, analysis code, data and figures. This is essential for open science and for the feasibility of replication study. The manuscript addresses the important topic of reproducibility and replication. Its well-written background section makes the paper not only of interest to this specific field, but also to a general audience. I recommend to publish the manuscript after some minor revisions:

Although the main purpose of the paper is replication, the other closely related topics should also be addressed. This includes:

- [x] Although the authors released their reproducibility packages, they don’t show the reproducibility of their calculations: can consistent results be generated when the calculations are repeated, how sensitive the results are to the input data, etc.
- [x]  What are the uncertainties of the calculations? Can error bars be added to the results as displayed in the figures and tables?

- [x] In the “replication of results from Rockstuhl, et al., 2005”, it appears that the main reason for the differences is the 2D and 3D representation between the previous and current studies. The authors show the impact of the y dimensions to the calculated results, but only use two lengths. Are there any limitations to to stop the authors to lengthen y larger than 2688 nm? Will some peaks disappear if the y dimension approaches to infinity?

Typos:
- [x] Page 5, line 30: PyGBE --> PyGBe
- [x] Page 18, line 18, “… he relationship …” --> “ … the relationship …”

**Response**

Running the execution scripts with the same input file on the same machine will produce the same results with bit-by-bit reproducibility. If running on a different machine, the results could show a difference due to floating-point error. We did confirm this. In fact, we have manually triggered correctness tests on the software that we run each time a change is applied in the code, which compares to previously generated results; we set these tests to pass when the difference in the results match to 10^{-10}.

The uncertainties in the calculations are: model uncertainties (quasi static approximation), spatial discretization errors (quantified via grid-convergence analysis in a previous paper that we cite in the manuscript), algebraic errors (from the iterative linear solver, set via exit tolerance), tree code approximation (quantifiable and controllable via expansion order and tree level). Additionally, the experimentally obtained value of the dielectric constant of the material is also subject to uncertainties (unknown to us). Since none of these sources of uncertainty is of statistical nature, error bars are not appropriate.

**Changes**

Added: "We did not explore larger values of $y$ because of the limitations imposed by the quasistatic limit model."

## Additional changes

After submission of the manuscript, and having posted the preprint on ArXiv, we received email communication from Prof. Carsten Rockstuhl, noting some refinements we could make to a couple of passages. We have documented this correspondence and the changes we made to the paper in [Issue 3](https://github.com/barbagroup/pygbe_validation_paper/issues/3) within our manuscript repository.

See history of commits, including:

- Commit [94279c6](https://github.com/barbagroup/pygbe_validation_paper/commit/94279c66d6654eebe2da4163689ac5d88ecd130a)
- Commit: [89b23f9](https://github.com/barbagroup/pygbe_validation_paper/commit/89b23f94f972d2c2bff5c1a899c407386de1ae48)

### 2020-10-21 tex/results.tex
tweak
fix typo in exponents, mesh densities

@@
 With that experience, and given the difficulty caused by sharp edges, we are content with studying grid-independence here instead.
-Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
- to 19,200 triangles (density $1.11\times10^{-5}$ per $\text{\AA}$ squared):
+Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-5}$ per $\text{\AA}$ squared)
+ to 19,200 triangles (density $1.11\times10^{-4}$ per $\text{\AA}$ squared):
  the computed results show no discernible difference.
@@
 values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
-intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
+intensity of some peaks decreases, due to the fact that they are associated to this component. Therefore, 
 from now on we use $y=2688$ nm. We did not explore larger values of $y$ because of the limitations imposed by the quasistatic limit model.

### 2021-01-31 tex/results.tex
fix broken Zenodo link

@@
 
-\item[$\triangleright$] The file sets for reproducing the figures for the validation and replication of results from Ellis et al., 2017 are arhived in Zenodo at \href{https://doi.org/3962797/zenodo.3962791}{10.5281/zenodo.3962797} \cite{ClementiBarba2020-Zen_e}.
+\item[$\triangleright$] The file sets for reproducing the figures for the validation and replication of results from Ellis et al., 2017 are arhived in Zenodo at \href{https://doi.org/10.5281/zenodo.3962797}{10.5281/zenodo.3962797} \cite{ClementiBarba2020-Zen_e}.
 

### 2021-01-31 tex/results.tex
changes due to editorial-office queries

@@
 \paragraph{Dielectric data:}
-The dielectric data for the simulations was given to us by the authors of the paper via a private communication, 
+The dielectric data for the simulations was given to us by the authors of the paper via a private communication  (CTE \& JGT, 2019), 
 and corresponds to experimental values of the dielectric.
@@
       \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
-      field is parallel to the length ($L$) of the pillar. We have normal incidence and 22-degree incidence.}
+      field is parallel to the length ($L$) of the pillar. We have normal incidence and 22-degree incidence. The wavelengths in bold correspond to the lowest mode that is not a longitudinal one.}
       \label{tab:ar_peaks}
@@
 If we use the same approximation and compare the results with the simulations of Ellis et al.\ on
-Figure 2 of their paper (green curve), we obtain Figure \ref{fig:rep_2a}.
+Figure 2  (green curve on their paper) we obtain Figure \ref{fig:rep_2a}.
 

### 2021-01-31 tex/discussion.tex
fix typos found in proof

@@
 
-Validation has been a hard goal to achieve for our solver since the field does not have benchmarks that are meant to be used for validation. Multiple times,
-we encountered experimental results that we aspired to replicate, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
+Validation has been a hard goal to achieve for our solver since the field does not have benchmarks that are meant to be used for this purpose. Multiple times,
+we encountered experimental results that we aspired to use for validation, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
 we have been unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 

### 2021-01-31 tex/results.tex
fix typos found in proof

@@
 cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$ nm) and varied length ($L=400$--$2800$ nm), for normal 
-and 22-degrees angle of incidence. The simulations where performed 
+and 22-degrees angle of incidence. The simulations were performed 
 for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
@@
 22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
-elongated size of the pillar.
+elongated side of the pillar.
 
